---
title: "Appendix"
format:  
  html:
    code-copy: true
    code-tools: true
    toc: true
    toc-location: right
    toc-depth: 4
    toc-expand: 2
    toc-title: Contents
    number-sections: true
    number-depth: 4 
    fig-width: 10  
    fig-height: 7
editor_options: 
  chunk_output_type: console
editor: source
fontsize: 12pt
---

```{r}
#| label: set
#| echo: false
#| messedad: false
#| warning: false

library(knitr)
knitr::opts_chunk$set(echo = FALSE, include = TRUE, warning = FALSE, messedad = FALSE)

table_format <- if(is_html_output()) {
  "html"
} else if(is_latex_output()) {
  "latex"
}
table_format2 <- if(is_html_output()) {
  T
} else if(is_latex_output()) {
  F
}

options(kableExtra.html.bsTable = T)
options(knitr.kable.NA = "")
```

# Voting

Variables:

- Participation in the 2013 elections (ola 1 y 2)

- Participation in the 2017 elections (ola 3 y 4)

- Participation in the constitutional plebiscite (ola 5)

- Participation in the 2021 election - First round (ola 6)

- Participation in the 2021 election - Runoff (ola 7)


```{r}
#if (!require("pacman")) install.packedads("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg,
               interactions,
               ggplot2,
               ggeffects
               )
load(file = here::here("input/data-proc/df_study1_long_t7.RData"))

# generate analytical sample
df_study1 <- 
  df_study1_long_t7 %>%
  select(idencuesta,ola,part_electoral, edad, sexo, pos_id, educ, universitaria, ponderador_long_total) %>% 
  na.omit() %>% 
  mutate(ola_num=as.numeric(ola),
         ola=as.factor(ola),
         edad = case_when(edad <=23~"Between 18 and 23",
                          edad >23 & edad <=28 ~ "Between 24 and 28",
                          edad >28 & edad <=45 ~ "Between 29 and 45",
                          edad > 45 ~ "More than 45")) 

df_study1$edad <- factor(df_study1$edad, levels = c("More than 45", "Between 29 and 45", "Between 24 and 28", "Between 18 and 23"))
df_study1$sexo <- factor(df_study1$sexo, levels = c(1, 2), labels = c("Man", "Woman"))
df_study1$educ <- factor(df_study1$educ,
                         levels = c("Media o menos", "Técnica", "Universitaria"),
                         labels = c("Secondary or less", "Technical", "University or more"))
df_study1$pos_id <- factor(df_study1$pos_id,
                         levels = c("Izquierda", "Centro", "Derecha", "No se identifica"),
                         labels = c("Left", "Center", "Right", "Doesn't identify"))

df_study1$part_electoral <- factor(df_study1$part_electoral, levels = c(1,2),
         labels = c("Yes", "No"))
df_study1$part_electoral <- car::recode(df_study1$part_electoral, c("1=2; 2=1"))
df_study1 <- df_study1 %>%
  dplyr::mutate(part_electoral = ifelse(part_electoral == "Yes", 1, 0))

# Hipotesis
h1 <- "ola"
h2 <- "ola+edad"
h3 <- "ola+edad+sexo"
h4 <- "ola+edad+sexo+educ"
h5 <- "ola+edad+sexo+educ+pos_id"
h6 <- "ola*edad+sexo+educ+pos_id"
h7 <- "ola*sexo+edad+sexo+educ+pos_id"
h8 <- "ola*educ+edad+sexo+educ+pos_id"
h9 <- "ola*pos_id+edad+sexo+educ+pos_id"
h10 <- "ola*pos_id*edad+sexo+educ+pos_id"
h11 <- "ola*educ*edad+sexo+educ+pos_id"
h12 <- "ola*sexo*edad+sexo+educ+pos_id"

marchar.null <- glmer(formula(paste0("part_electoral~","1 + (1|idencuesta)")),data = df_study1, weights = ponderador_long_total, family = "binomial")
marchar1 <- glmer(formula(paste0("part_electoral~",h1,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total, family = "binomial")
marchar2 <- glmer(formula(paste0("part_electoral~",h2,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total, family = "binomial")
marchar3 <- glmer(formula(paste0("part_electoral~",h3,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total, family = "binomial")
marchar4 <- lmer(formula(paste0("part_electoral~",h4,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar5 <- lmer(formula(paste0("part_electoral~",h5,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar6 <- lmer(formula(paste0("part_electoral~",h6,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar7 <- lmer(formula(paste0("part_electoral~",h7,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar8 <- lmer(formula(paste0("part_electoral~",h8,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar9 <- lmer(formula(paste0("part_electoral~",h9,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar10 <- lmer(formula(paste0("part_electoral~",h10,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar11 <- lmer(formula(paste0("part_electoral~",h11,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar12 <- lmer(formula(paste0("part_electoral~",h12,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)

```

## Main effects

```{r results='asis'}
ccoef <- list(
  "(Intercept)" = "Intercept",
  "ola2" = "2017",
  "ola3" = "2018",
  "ola4" = "2019",
  "ola5" = "2021",
  "ola6" = "2022",
  "ola7" = "2023",
  "edadBetween 29 and 45" = "Between 29 and 45",
  "edadBetween 24 and 28" = "Between 24 and 28",
  "edadBetween 18 and 23" = "Between 18 and 23",
  "sexoWoman" = "Woman (Ref.= Man)",
  "educTechnical" = "Technical",
  "educUniversity or more" = "University or more",
  "pos_idCenter" = "Center",
  "pos_idRight" = "Right",
  "pos_idDoesn't identify" = "Doesn't identify"
  )

texreg::knitreg(list(marchar1, marchar2, marchar3, marchar4, marchar5),
               custom.model.names = c(paste0("Model ", seq(1:5))),
               caption.above = T,
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef,
               digits = 2,
               groups = list("Wave (Ref.= 2016)" = 2:7,
                             "Age (Ref.= More than 45)" = 8:10,
                             "Education (Ref.= Secondary)" = 12:13,
                             "Political position (Ref.= Left)" = 14:16),
               custom.note = "Note: Cells contain regression coefficients with standard errors in parentheses. \n %stars.",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.80,
               include.loglik = FALSE,
               include.aic = FALSE,
               center = T,
               custom.gof.names = c("BIC", "Numb. obs.", "Num. groups: individuals", "Var: individuals (Intercept)", "Var: Residual")
               )
```

## Interactions effects 

```{r results='asis'}
ccoef2 <- list(
  "(Intercept)" = "Intercept",
  "ola2:edadBetween 29 and 45" = "2017*Age 29-45",
  "ola3:edadBetween 29 and 45" = "2018*Age 29-45",
  "ola4:edadBetween 29 and 45" = "2019*Age 29-45",
  "ola5:edadBetween 29 and 45" = "2021*Age 29-45",
  "ola6:edadBetween 29 and 45" = "2022*Age 29-45",
  "ola7:edadBetween 29 and 45" = "2023*Age 29-45",
  "ola2:edadBetween 24 and 28" = "2017*Age 24-28",
  "ola3:edadBetween 24 and 28" = "2018*Age 24-28",
  "ola4:edadBetween 24 and 28" = "2019*Age 24-28",
  "ola5:edadBetween 24 and 28" = "2021*Age 24-28",
  "ola6:edadBetween 24 and 28" = "2022*Age 24-28",
  "ola7:edadBetween 24 and 28" = "2023*Age 24-28",
  "ola2:edadBetween 18 and 23" = "2017*Age 18-23",
  "ola3:edadBetween 18 and 23" = "2018*Age 18-23",
  "ola4:edadBetween 18 and 23" = "2019*Age 18-23",
  "ola5:edadBetween 18 and 23" = "2021*Age 18-23",
  "ola6:edadBetween 18 and 23" = "2022*Age 18-23",
  "ola7:edadBetween 18 and 23" = "2023*Age 18-23",
  "ola2:sexoWoman" = "2017*Woman",
  "ola3:sexoWoman" = "2018*Woman",
  "ola4:sexoWoman" = "2019*Woman",
  "ola5:sexoWoman" = "2021*Woman",
  "ola6:sexoWoman" = "2022*Woman",
  "ola7:sexoWoman" = "2023*Woman",
  "ola2:educTechnical" = "2017*Technical",
  "ola3:educTechnical" = "2018*Technical",
  "ola4:educTechnical" = "2019*Technical",
  "ola5:educTechnical" = "2021*Technical",
  "ola6:educTechnical" = "2022*Technical",
  "ola7:educTechnical" = "2023*Technical",
  "ola2:educUniversity or more" = "2017*University",
  "ola3:educUniversity or more" = "2018*University",
  "ola4:educUniversity or more" = "2019*University",
  "ola5:educUniversity or more" = "2021*University",
  "ola6:educUniversity or more" = "2022*University",
  "ola7:educUniversity or more" = "2023*University",
  "ola2:pos_idCenter" = "2017*Center",
  "ola3:pos_idCenter" = "2018*Center",
  "ola4:pos_idCenter" = "2019*Center",
  "ola5:pos_idCenter" = "2021*Center",
  "ola6:pos_idCenter" = "2022*Center",
  "ola7:pos_idCenter" = "2023*Center",
  "ola2:pos_idRight" = "2017*Right",
  "ola3:pos_idRight" = "2018*Right",
  "ola4:pos_idRight" = "2019*Right",
  "ola5:pos_idRight" = "2021*Right",
  "ola6:pos_idRight" = "2022*Right",
  "ola7:pos_idRight" = "2023*Right",
  "ola2:pos_idDoesn't identify" = "2017*Doesn't identify",
  "ola3:pos_idDoesn't identify" = "2018*Doesn't identify",
  "ola4:pos_idDoesn't identify" = "2019*Doesn't identify",
  "ola5:pos_idDoesn't identify" = "2021*Doesn't identify",
  "ola6:pos_idDoesn't identify" = "2022*Doesn't identify",
  "ola7:pos_idDoesn't identify" = "2023*Doesn't identify",
  "pos_idCenter:edadBetween 29 and 45" = "Center*Age 29-45",
  "pos_idRight:edadBetween 29 and 45" = "Right*Age 29-45",
  "pos_idDoesn't identify:edadBetween 29 and 45" = "Doesn't identify * Age 29-45",
  "pos_idCenter:edadBetween 29 and 45" = "Center*Age 24-28",
  "pos_idRight:edadBetween 29 and 45" = "Right*Age 24-28",
  "pos_idDoesn't identify:edadBetween 29 and 45" = "Doesn't identify * Age 24-28",
  "pos_idCenter:edadBetween 29 and 45" = "Center*Age 18-23",
  "pos_idRight:edadBetween 29 and 45" = "Right*Age 18-23",
  "pos_idDoesn't identify:edadBetween 29 and 45" = "Doesn't identify * Age 18-23",
  "ola2:pos_idCenter:edadBetween 29 and 45" = "2017 * Center * Age 29-45",
  "ola3:pos_idCenter:edadBetween 29 and 45" = "2018 * Center * Age 29-45",
  "ola4:pos_idCenter:edadBetween 29 and 45" = "2019 * Center * Age 29-45",
  "ola5:pos_idCenter:edadBetween 29 and 45" = "2021 * Center * Age 29-45",
  "ola6:pos_idCenter:edadBetween 29 and 45" = "2022 * Center * Age 29-45",
  "ola7:pos_idCenter:edadBetween 29 and 45" = "2023 * Center * Age 29-45",
  "ola2:pos_idRight:edadBetween 29 and 45" = "2017 * Right * Age 29-45",
  "ola3:pos_idRight:edadBetween 29 and 45" = "2018 * Right * Age 29-45",
  "ola4:pos_idRight:edadBetween 29 and 45" = "2019 * Right * Age 29-45",
  "ola5:pos_idRight:edadBetween 29 and 45" = "2021 * Right * Age 29-45",
  "ola6:pos_idRight:edadBetween 29 and 45" = "2022 * Right * Age 29-45",
  "ola7:pos_idRight:edadBetween 29 and 45" = "2023 * Right * Age 29-45",
  "ola2:pos_idDoesn't identify:edadBetween 29 and 45" = "2017 * Doesn't identify * Age 29-45",
  "ola3:pos_idDoesn't identify:edadBetween 29 and 45" = "2018 * Doesn't identify * Age 29-45",
  "ola4:pos_idDoesn't identify:edadBetween 29 and 45" = "2019 * Doesn't identify * Age 29-45",
  "ola5:pos_idDoesn't identify:edadBetween 29 and 45" = "2021 * Doesn't identify * Age 29-45",
  "ola6:pos_idDoesn't identify:edadBetween 29 and 45" = "2022 * Doesn't identify * Age 29-45",
  "ola7:pos_idDoesn't identify:edadBetween 29 and 45" = "2023 * Doesn't identify * Age 29-45",
  "ola2:pos_idCenter:edadBetween 24 and 28" = "2017 * Center * Age 24-28",
  "ola3:pos_idCenter:edadBetween 24 and 28" = "2018 * Center * Age 24-28",
  "ola4:pos_idCenter:edadBetween 24 and 28" = "2019 * Center * Age 24-28",
  "ola5:pos_idCenter:edadBetween 24 and 28" = "2021 * Center * Age 24-28",
  "ola6:pos_idCenter:edadBetween 24 and 28" = "2022 * Center * Age 24-28",
  "ola7:pos_idCenter:edadBetween 24 and 28" = "2023 * Center * Age 24-28",
  "ola2:pos_idRight:edadBetween 24 and 28" = "2017 * Right * Age 24-28",
  "ola3:pos_idRight:edadBetween 24 and 28" = "2018 * Right * Age 24-28",
  "ola4:pos_idRight:edadBetween 24 and 28" = "2019 * Right * Age 24-28",
  "ola5:pos_idRight:edadBetween 24 and 28" = "2021 * Right * Age 24-28",
  "ola6:pos_idRight:edadBetween 24 and 28" = "2022 * Right * Age 24-28",
  "ola7:pos_idRight:edadBetween 24 and 28" = "2023 * Right * Age 24-28",
  "ola2:pos_idDoesn't identify:edadBetween 24 and 28" = "2017 * Doesn't identify * Age 24-28",
  "ola3:pos_idDoesn't identify:edadBetween 24 and 28" = "2018 * Doesn't identify * Age 24-28",
  "ola4:pos_idDoesn't identify:edadBetween 24 and 28" = "2019 * Doesn't identify * Age 24-28",
  "ola5:pos_idDoesn't identify:edadBetween 24 and 28" = "2021 * Doesn't identify * Age 24-28",
  "ola6:pos_idDoesn't identify:edadBetween 24 and 28" = "2022 * Doesn't identify * Age 24-28",
  "ola7:pos_idDoesn't identify:edadBetween 24 and 28" = "2023 * Doesn't identify * Age 24-28",
  "ola2:pos_idCenter:edadBetween 18 and 23" = "2017 * Center * Age 18-23",
  "ola3:pos_idCenter:edadBetween 18 and 23" = "2018 * Center * Age 18-23",
  "ola4:pos_idCenter:edadBetween 18 and 23" = "2019 * Center * Age 18-23",
  "ola5:pos_idCenter:edadBetween 18 and 23" = "2021 * Center * Age 18-23",
  "ola6:pos_idCenter:edadBetween 18 and 23" = "2022 * Center * Age 18-23",
  "ola7:pos_idCenter:edadBetween 18 and 23" = "2023 * Center * Age 18-23",
  "ola2:pos_idRight:edadBetween 18 and 23" = "2017 * Right * Age 18-23",
  "ola3:pos_idRight:edadBetween 18 and 23" = "2018 * Right * Age 18-23",
  "ola4:pos_idRight:edadBetween 18 and 23" = "2019 * Right * Age 18-23",
  "ola5:pos_idRight:edadBetween 18 and 23" = "2021 * Right * Age 18-23",
  "ola6:pos_idRight:edadBetween 18 and 23" = "2022 * Right * Age 18-23",
  "ola7:pos_idRight:edadBetween 18 and 23" = "2023 * Right * Age 18-23",
  "ola2:pos_idDoesn't identify:edadBetween 18 and 23" = "2017 * Doesn't identify * Age 18-23",
  "ola3:pos_idDoesn't identify:edadBetween 18 and 23" = "2018 * Doesn't identify * Age 18-23",
  "ola4:pos_idDoesn't identify:edadBetween 18 and 23" = "2019 * Doesn't identify * Age 18-23",
  "ola5:pos_idDoesn't identify:edadBetween 18 and 23" = "2021 * Doesn't identify * Age 18-23",
  "ola6:pos_idDoesn't identify:edadBetween 18 and 23" = "2022 * Doesn't identify * Age 18-23",
  "ola7:pos_idDoesn't identify:edadBetween 18 and 23" = "2023 * Doesn't identify * Age 18-23",
  "educTechnical:edadBetween 29 and 45" = "Technical * Age 29-45",
  "educUniversity or more:edadBetween 29 and 45" = "University * Age 29-45",
  "educTechnical:edadBetween 24 and 28" = "Technical * Age 24-28",
  "educUniversity or more:edadBetween 24 and 28" = "University * Age 24-28",
  "educTechnical:edadBetween 18 and 23" = "Technical * Age 18-23",
  "educUniversity or more:edadBetween 18 and 23" = "University * Age 18-23",
  "ola2:educTechnical:edadBetween 29 and 45" = "2017 * Technical * Age 29-45",
  "ola3:educTechnical:edadBetween 29 and 45" = "2018 * Technical * Age 29-45",
  "ola4:educTechnical:edadBetween 29 and 45" = "2019 * Technical * Age 29-45",
  "ola5:educTechnical:edadBetween 29 and 45" = "2021 * Technical * Age 29-45",
  "ola6:educTechnical:edadBetween 29 and 45" = "2022 * Technical * Age 29-45",
  "ola7:educTechnical:edadBetween 29 and 45" = "2023 * Technical * Age 29-45",
  "ola2:educUniversity or more:edadBetween 29 and 45" = "2017 * University * Age 29-45",
  "ola3:educUniversity or more:edadBetween 29 and 45" = "2018 * University * Age 29-45",
  "ola4:educUniversity or more:edadBetween 29 and 45" = "2019 * University * Age 29-45",
  "ola5:educUniversity or more:edadBetween 29 and 45" = "2021 * University * Age 29-45",
  "ola6:educUniversity or more:edadBetween 29 and 45" = "2022 * University * Age 29-45",
  "ola7:educUniversity or more:edadBetween 29 and 45" = "2023 * University * Age 29-45",
  "ola2:educTechnical:edadBetween 24 and 28" = "2017 * Technical * Age 24-28",
  "ola3:educTechnical:edadBetween 24 and 28" = "2018 * Technical * Age 24-28",
  "ola4:educTechnical:edadBetween 24 and 28" = "2019 * Technical * Age 24-28",
  "ola5:educTechnical:edadBetween 24 and 28" = "2021 * Technical * Age 24-28",
  "ola6:educTechnical:edadBetween 24 and 28" = "2022 * Technical * Age 24-28",
  "ola7:educTechnical:edadBetween 24 and 28" = "2023 * Technical * Age 24-28",
  "ola2:educUniversity or more:edadBetween 24 and 28" = "2017 * University * Age 24-28",
  "ola3:educUniversity or more:edadBetween 24 and 28" = "2018 * University * Age 24-28",
  "ola4:educUniversity or more:edadBetween 24 and 28" = "2019 * University * Age 24-28",
  "ola5:educUniversity or more:edadBetween 24 and 28" = "2021 * University * Age 24-28",
  "ola6:educUniversity or more:edadBetween 24 and 28" = "2022 * University * Age 24-28",
  "ola7:educUniversity or more:edadBetween 24 and 28" = "2023 * University * Age 24-28",
  "ola2:educTechnical:edadBetween 18 and 23" = "2017 * Technical * Age 18-23",
  "ola3:educTechnical:edadBetween 18 and 23" = "2018 * Technical * Age 18-23",
  "ola4:educTechnical:edadBetween 18 and 23" = "2019 * Technical * Age 18-23",
  "ola5:educTechnical:edadBetween 18 and 23" = "2021 * Technical * Age 18-23",
  "ola6:educTechnical:edadBetween 18 and 23" = "2022 * Technical * Age 18-23",
  "ola7:educTechnical:edadBetween 18 and 23" = "2023 * Technical * Age 18-23",
  "ola2:educUniversity or more:edadBetween 18 and 23" = "2017 * University * Age 18-23",
  "ola3:educUniversity or more:edadBetween 18 and 23" = "2018 * University * Age 18-23",
  "ola4:educUniversity or more:edadBetween 18 and 23" = "2019 * University * Age 18-23",
  "ola5:educUniversity or more:edadBetween 18 and 23" = "2021 * University * Age 18-23",
  "ola6:educUniversity or more:edadBetween 18 and 23" = "2022 * University * Age 18-23",
  "ola7:educUniversity or more:edadBetween 18 and 23" = "2023 * University * Age 18-23",
  "sexoWoman:edadBetween 29 and 45" = "Woman * Age 29-45",
  "sexoWoman:edadBetween 29 and 45" = "Woman * Age 24-28",
  "sexoWoman:edadBetween 29 and 45" = "Woman * Age 18-23",
  "ola2:sexoWoman:edadBetween 29 and 45" = "2017 * Woman * Age 29-45",
  "ola3:sexoWoman:edadBetween 29 and 45" = "2018 * Woman * Age 29-45",
  "ola4:sexoWoman:edadBetween 29 and 45" = "2019 * Woman * Age 29-45",
  "ola5:sexoWoman:edadBetween 29 and 45" = "2021 * Woman * Age 29-45",
  "ola6:sexoWoman:edadBetween 29 and 45" = "2022 * Woman * Age 29-45",
  "ola7:sexoWoman:edadBetween 29 and 45" = "2023 * Woman * Age 29-45",
  "ola2:sexoWoman:edadBetween 24 and 28" = "2017 * Woman * Age 24-28",
  "ola3:sexoWoman:edadBetween 24 and 28" = "2018 * Woman * Age 24-28",
  "ola4:sexoWoman:edadBetween 24 and 28" = "2019 * Woman * Age 24-28",
  "ola5:sexoWoman:edadBetween 24 and 28" = "2021 * Woman * Age 24-28",
  "ola6:sexoWoman:edadBetween 24 and 28" = "2022 * Woman * Age 24-28",
  "ola7:sexoWoman:edadBetween 24 and 28" = "2023 * Woman * Age 24-28",
  "ola2:sexoWoman:edadBetween 18 and 23" = "2017 * Woman * Age 18-23",
  "ola3:sexoWoman:edadBetween 18 and 23" = "2018 * Woman * Age 18-23",
  "ola4:sexoWoman:edadBetween 18 and 23" = "2019 * Woman * Age 18-23",
  "ola5:sexoWoman:edadBetween 18 and 23" = "2021 * Woman * Age 18-23",
  "ola6:sexoWoman:edadBetween 18 and 23" = "2022 * Woman * Age 18-23",
  "ola7:sexoWoman:edadBetween 18 and 23" = "2023 * Woman * Age 18-23"
  )

texreg::knitreg(list(marchar6, marchar7, marchar8, marchar9, marchar10, marchar11,marchar12),
               custom.model.names = c(paste0("Model ", seq(6:12))),
               caption.above = T,
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef2,
               digits = 2,
               custom.note = "Note: Cells contain regression coefficients with standard errors in parentheses. \n %stars.",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.80,
               include.loglik = FALSE,
               include.aic = FALSE,
               center = T,
               custom.gof.names = c("BIC", "Numb. obs.", "Num. groups: individuals", "Var: individuals (Intercept)", "Var: Residual"))
```

### Resume table

```{r}
betas <- marchar12@beta                           # Coeficientes
vcov_mat <- as.matrix(vcov(marchar12))              # Matriz de varianzas-covarianzas
ses <- sqrt(diag(vcov_mat))                         # Errores estándar
tvals <- betas / ses                              # Valores t

ses <- ses[44:61]
betas <- betas[44:61]
tvals <- tvals[44:61]

pvals <- 2 * pnorm(-abs(tvals))  # Aproximación tipo Wald (z-score)

signif_stars <- ifelse(pvals <= 0.001, "***",
                 ifelse(pvals <= 0.01, "**",
                 ifelse(pvals <= 0.05, "*", "")))

olasexoedad<-data.frame(
  Estimate = betas,
  Signif = signif_stars
)


betas <- marchar11@beta                          # Coeficientes
vcov_mat <- as.matrix(vcov(marchar11))              # Matriz de varianzas-covarianzas
ses <- sqrt(diag(vcov_mat))                         # Errores estándar
tvals <- betas / ses                              # Valores t

ses <- ses[53:88]
betas <- betas[53:88]
tvals <- tvals[53:88]

pvals <- 2 * pnorm(-abs(tvals))  # Aproximación tipo Wald (z-score)

signif_stars <- ifelse(pvals <= 0.001, "***",
                 ifelse(pvals <= 0.01, "**",
                 ifelse(pvals <= 0.05, "*", "")))

olaeducedad<-data.frame(
  Estimate = betas,
  Signif = signif_stars
)


betas <- marchar10@beta                          # Coeficientes
vcov_mat <- as.matrix(vcov(marchar10))              # Matriz de varianzas-covarianzas
ses <- sqrt(diag(vcov_mat))                         # Errores estándar
tvals <- betas / ses                              # Valores t

ses <- ses[62:115]
betas <- betas[62:115]
tvals <- tvals[62:115]

pvals <- 2 * pnorm(-abs(tvals))  # Aproximación tipo Wald (z-score)

signif_stars <- ifelse(pvals <= 0.001, "***",
                 ifelse(pvals <= 0.01, "**",
                 ifelse(pvals <= 0.05, "*", "")))

olapospoledad<-data.frame(
  Estimate = betas,
  Signif = signif_stars
)

# Woman (olasexoedad)
woman_idx <- c(1, 7, 13, 2, 8, 14, 3, 9, 15, 4, 10, 16, 5, 11, 17, 6, 12, 18)

# Technical (olaeducedad)
technical_idx <- c(1, 13, 25, 2, 14, 26, 3, 15, 27, 4, 16, 28, 5, 17, 29, 6, 18, 30)

# University (olaeducedad)
university_idx <- c(7, 19, 31, 8, 20, 32, 9, 21, 33, 10, 22, 34, 11, 23, 35, 12, 24, 36)

# Edad 29–45 → posiciones: 1, 19, 37, 2, 20, 38, 3, 21, 39, ...
center_idx <- c(1, 19, 37, 2, 20, 38, 3, 21, 39, 4, 22, 40, 5, 23, 41, 6, 24, 42)
right_idx  <- c(7, 25, 43, 8, 26, 44, 9, 27, 45,10, 28, 46,11, 29, 47,12, 30, 48)
dni_idx    <- c(13, 31, 49,14, 32, 50,15, 33, 51,16, 34, 52,17, 35, 53,18, 36, 54)




tabla <- cbind(
  Year = c("2017", "2017", "2017", 
          "2018", "2018", "2018",
          "2019", "2019", "2019",
          "2021", "2021", "2021", 
          "2022", "2022", "2022", 
          "2023", "2023", "2023"),
  Age = rep(c("29–45", "24–28", "18–23"), times = 6),
  Woman = paste0(round(olasexoedad$Estimate[woman_idx], 2), olasexoedad$Signif[woman_idx]),
  Technical = paste0(round(olaeducedad$Estimate[technical_idx], 2), olaeducedad$Signif[technical_idx]),
  University = paste0(round(olaeducedad$Estimate[university_idx], 2), olaeducedad$Signif[university_idx]),
  Center = paste0(round(olapospoledad$Estimate[center_idx], 2), olapospoledad$Signif[center_idx]),
  Right = paste0(round(olapospoledad$Estimate[right_idx], 2), olapospoledad$Signif[right_idx]),
  `Doesnt Identify` = paste0(round(olapospoledad$Estimate[dni_idx], 2), olapospoledad$Signif[dni_idx])
)
```

```{r}
kbl(tabla, 
    align = "c") %>% 
    add_header_above(c(" " = 3,
                     "Education"=2, 
                     "Political position"=3),
                   bold = T)%>%  
  kable_paper("hover",full_width = F) %>%
     column_spec(1, bold = T) %>%
     collapse_rows(columns = 1, valign = "middle") %>% 
  footnote("***p < 0.001; **p < 0.01; *p < 0.05.")
```

## Interaction effects graphs

- Voting and age

```{r}
elecciones<- c("Elections
2013", "Elections
2013", "Elections
2017", "Elections
2017", "Constitutional 
plebiscite","Election first
round 2021", "Election runoff
2021")

preds <- ggpredict(marchar6, terms = c("ola", "edad"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
 # facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Electoral participation",
    color = "Age"
  ) +
  ylim(0, 1) +
  scale_x_discrete(labels = elecciones) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Voting and sex

```{r}
preds <- ggpredict(marchar7, terms = c("ola", "sexo"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
 # facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Electoral participation",
    color = "Sex"
  ) +
  ylim(0, 1) +
  scale_x_discrete(labels = elecciones) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Voting, age and sex

```{r}
preds <- ggpredict(marchar12, terms = c("ola", "edad", "sexo"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Electoral participation",
    color = "Age"
  ) +
  ylim(0, 1) +
  scale_x_discrete(labels = elecciones) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Voting and Education

```{r}
preds <- ggpredict(marchar8, terms = c("ola", "educ"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
#  facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Electoral participation",
    color = "Education"
  ) +
  ylim(0,1) +
  scale_x_discrete(labels = elecciones) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Voting, age and education

```{r}
preds <- ggpredict(marchar11, terms = c("ola", "edad", "educ"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Electoral participation",
    color = "edad"
  ) +
  ylim(0, 1.2) +
  scale_x_discrete(labels = elecciones) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Voting and political position

```{r}
preds <- ggpredict(marchar9, terms = c("ola", "pos_id"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
#  facet_wrap(~ facet, ncol = 3) +
  labs(
    x = "Year",
    y = "Electoral participation",
    color = "Political position"
  ) +
  ylim(0, 1) +
  scale_x_discrete(labels = elecciones) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Voting, age and political position

```{r}
preds <- ggpredict(marchar10, terms = c("ola", "edad", "pos_id"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Electoral participation",
    color = "edad"
  ) +
  ylim(0, 1) +
  scale_x_discrete(labels = elecciones) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

# Participation online

```{r}
if (!require("pacman")) install.packedads("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg
               )
load(file = here::here("input/data-proc/df_study1_long_t7.RData"))

# generate analytical sample
df_study1 <- 
  df_study1_long_t7 %>%
  select(idencuesta,ola,part_rrss, edad, sexo, pos_id, educ, universitaria, ponderador_long_total) %>% 
  na.omit() %>% 
  mutate(ola_num=as.numeric(ola),
         ola=as.factor(ola),
         edad = case_when(edad <=23~"Between 18 and 23",
                          edad >23 & edad <=28 ~ "Between 24 and 28",
                          edad >28 & edad <=45 ~ "Between 29 and 45",
                          edad > 45 ~ "More than 45")) 

df_study1$edad <- factor(df_study1$edad, levels = c("More than 45", "Between 29 and 45", "Between 24 and 28", "Between 18 and 23"))
df_study1$sexo <- factor(df_study1$sexo, levels = c(1, 2), labels = c("Man", "Woman"))
df_study1$educ <- factor(df_study1$educ,
                         levels = c("Media o menos", "Técnica", "Universitaria"),
                         labels = c("Secondary or less", "Technical", "University or more"))
df_study1$pos_id <- factor(df_study1$pos_id,
                         levels = c("Izquierda", "Centro", "Derecha", "No se identifica"),
                         labels = c("Left", "Center", "Right", "Doesn't identify"))

marchar.null <- lmer(formula(paste0("part_rrss~","1 + (1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar1 <- lmer(formula(paste0("part_rrss~",h1,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar2 <- lmer(formula(paste0("part_rrss~",h2,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar3 <- lmer(formula(paste0("part_rrss~",h3,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar4 <- lmer(formula(paste0("part_rrss~",h4,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar5 <- lmer(formula(paste0("part_rrss~",h5,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar6 <- lmer(formula(paste0("part_rrss~",h6,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar7 <- lmer(formula(paste0("part_rrss~",h7,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar8 <- lmer(formula(paste0("part_rrss~",h8,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar9 <- lmer(formula(paste0("part_rrss~",h9,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar10 <- lmer(formula(paste0("part_rrss~",h10,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar11 <- lmer(formula(paste0("part_rrss~",h11,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar12 <- lmer(formula(paste0("part_rrss~",h12,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
```

## Main effects

```{r results='asis'}
ccoef <- list(
  "(Intercept)" = "Intercept",
  "ola2" = "2017",
  "ola3" = "2018",
  "ola4" = "2019",
  "ola5" = "2021",
  "ola6" = "2022",
  "ola7" = "2023",
  "edadBetween 29 and 45" = "Between 29 and 45",
  "edadBetween 24 and 28" = "Between 24 and 28",
  "edadBetween 18 and 23" = "Between 18 and 23",
  "sexoWoman" = "Woman (Ref.= Man)",
  "educTechnical" = "Technical",
  "educUniversity or more" = "University or more",
  "pos_idCenter" = "Center",
  "pos_idRight" = "Right",
  "pos_idDoesn't identify" = "Doesn't identify"
  )

texreg::knitreg(list(marchar1, marchar2, marchar3, marchar4, marchar5),
               custom.model.names = c(paste0("Model ", seq(1:5))),
               caption.above = T,
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef,
               digits = 2,
               groups = list("Wave (Ref.= 2016)" = 2:7,
                             "Age (Ref.= More than 45)" = 8:10,
                             "Education (Ref.= Secondary)" = 12:13,
                             "Political position (Ref.= Left)" = 14:16),
               custom.note = "Note: Cells contain regression coefficients with standard errors in parentheses. \n %stars.",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.80,
               include.loglik = FALSE,
               include.aic = FALSE,
               center = T,
               custom.gof.names = c("BIC", "Numb. obs.", "Num. groups: individuals", "Var: individuals (Intercept)", "Var: Residual")
               )
```

## Interaction effects

```{r results='asis'}
ccoef2 <- list(
  "(Intercept)" = "Intercept",
  "ola2:edadBetween 29 and 45" = "2017*Age 29-45",
  "ola3:edadBetween 29 and 45" = "2018*Age 29-45",
  "ola4:edadBetween 29 and 45" = "2019*Age 29-45",
  "ola5:edadBetween 29 and 45" = "2021*Age 29-45",
  "ola6:edadBetween 29 and 45" = "2022*Age 29-45",
  "ola7:edadBetween 29 and 45" = "2023*Age 29-45",
  "ola2:edadBetween 24 and 28" = "2017*Age 24-28",
  "ola3:edadBetween 24 and 28" = "2018*Age 24-28",
  "ola4:edadBetween 24 and 28" = "2019*Age 24-28",
  "ola5:edadBetween 24 and 28" = "2021*Age 24-28",
  "ola6:edadBetween 24 and 28" = "2022*Age 24-28",
  "ola7:edadBetween 24 and 28" = "2023*Age 24-28",
  "ola2:edadBetween 18 and 23" = "2017*Age 18-23",
  "ola3:edadBetween 18 and 23" = "2018*Age 18-23",
  "ola4:edadBetween 18 and 23" = "2019*Age 18-23",
  "ola5:edadBetween 18 and 23" = "2021*Age 18-23",
  "ola6:edadBetween 18 and 23" = "2022*Age 18-23",
  "ola7:edadBetween 18 and 23" = "2023*Age 18-23",
  "ola2:sexoWoman" = "2017*Woman",
  "ola3:sexoWoman" = "2018*Woman",
  "ola4:sexoWoman" = "2019*Woman",
  "ola5:sexoWoman" = "2021*Woman",
  "ola6:sexoWoman" = "2022*Woman",
  "ola7:sexoWoman" = "2023*Woman",
  "ola2:educTechnical" = "2017*Technical",
  "ola3:educTechnical" = "2018*Technical",
  "ola4:educTechnical" = "2019*Technical",
  "ola5:educTechnical" = "2021*Technical",
  "ola6:educTechnical" = "2022*Technical",
  "ola7:educTechnical" = "2023*Technical",
  "ola2:educUniversity or more" = "2017*University",
  "ola3:educUniversity or more" = "2018*University",
  "ola4:educUniversity or more" = "2019*University",
  "ola5:educUniversity or more" = "2021*University",
  "ola6:educUniversity or more" = "2022*University",
  "ola7:educUniversity or more" = "2023*University",
  "ola2:pos_idCenter" = "2017*Center",
  "ola3:pos_idCenter" = "2018*Center",
  "ola4:pos_idCenter" = "2019*Center",
  "ola5:pos_idCenter" = "2021*Center",
  "ola6:pos_idCenter" = "2022*Center",
  "ola7:pos_idCenter" = "2023*Center",
  "ola2:pos_idRight" = "2017*Right",
  "ola3:pos_idRight" = "2018*Right",
  "ola4:pos_idRight" = "2019*Right",
  "ola5:pos_idRight" = "2021*Right",
  "ola6:pos_idRight" = "2022*Right",
  "ola7:pos_idRight" = "2023*Right",
  "ola2:pos_idDoesn't identify" = "2017*Doesn't identify",
  "ola3:pos_idDoesn't identify" = "2018*Doesn't identify",
  "ola4:pos_idDoesn't identify" = "2019*Doesn't identify",
  "ola5:pos_idDoesn't identify" = "2021*Doesn't identify",
  "ola6:pos_idDoesn't identify" = "2022*Doesn't identify",
  "ola7:pos_idDoesn't identify" = "2023*Doesn't identify",
  "pos_idCenter:edadBetween 29 and 45" = "Center*Age 29-45",
  "pos_idRight:edadBetween 29 and 45" = "Right*Age 29-45",
  "pos_idDoesn't identify:edadBetween 29 and 45" = "Doesn't identify * Age 29-45",
  "pos_idCenter:edadBetween 29 and 45" = "Center*Age 24-28",
  "pos_idRight:edadBetween 29 and 45" = "Right*Age 24-28",
  "pos_idDoesn't identify:edadBetween 29 and 45" = "Doesn't identify * Age 24-28",
  "pos_idCenter:edadBetween 29 and 45" = "Center*Age 18-23",
  "pos_idRight:edadBetween 29 and 45" = "Right*Age 18-23",
  "pos_idDoesn't identify:edadBetween 29 and 45" = "Doesn't identify * Age 18-23",
  "ola2:pos_idCenter:edadBetween 29 and 45" = "2017 * Center * Age 29-45",
  "ola3:pos_idCenter:edadBetween 29 and 45" = "2018 * Center * Age 29-45",
  "ola4:pos_idCenter:edadBetween 29 and 45" = "2019 * Center * Age 29-45",
  "ola5:pos_idCenter:edadBetween 29 and 45" = "2021 * Center * Age 29-45",
  "ola6:pos_idCenter:edadBetween 29 and 45" = "2022 * Center * Age 29-45",
  "ola7:pos_idCenter:edadBetween 29 and 45" = "2023 * Center * Age 29-45",
  "ola2:pos_idRight:edadBetween 29 and 45" = "2017 * Right * Age 29-45",
  "ola3:pos_idRight:edadBetween 29 and 45" = "2018 * Right * Age 29-45",
  "ola4:pos_idRight:edadBetween 29 and 45" = "2019 * Right * Age 29-45",
  "ola5:pos_idRight:edadBetween 29 and 45" = "2021 * Right * Age 29-45",
  "ola6:pos_idRight:edadBetween 29 and 45" = "2022 * Right * Age 29-45",
  "ola7:pos_idRight:edadBetween 29 and 45" = "2023 * Right * Age 29-45",
  "ola2:pos_idDoesn't identify:edadBetween 29 and 45" = "2017 * Doesn't identify * Age 29-45",
  "ola3:pos_idDoesn't identify:edadBetween 29 and 45" = "2018 * Doesn't identify * Age 29-45",
  "ola4:pos_idDoesn't identify:edadBetween 29 and 45" = "2019 * Doesn't identify * Age 29-45",
  "ola5:pos_idDoesn't identify:edadBetween 29 and 45" = "2021 * Doesn't identify * Age 29-45",
  "ola6:pos_idDoesn't identify:edadBetween 29 and 45" = "2022 * Doesn't identify * Age 29-45",
  "ola7:pos_idDoesn't identify:edadBetween 29 and 45" = "2023 * Doesn't identify * Age 29-45",
  "ola2:pos_idCenter:edadBetween 24 and 28" = "2017 * Center * Age 24-28",
  "ola3:pos_idCenter:edadBetween 24 and 28" = "2018 * Center * Age 24-28",
  "ola4:pos_idCenter:edadBetween 24 and 28" = "2019 * Center * Age 24-28",
  "ola5:pos_idCenter:edadBetween 24 and 28" = "2021 * Center * Age 24-28",
  "ola6:pos_idCenter:edadBetween 24 and 28" = "2022 * Center * Age 24-28",
  "ola7:pos_idCenter:edadBetween 24 and 28" = "2023 * Center * Age 24-28",
  "ola2:pos_idRight:edadBetween 24 and 28" = "2017 * Right * Age 24-28",
  "ola3:pos_idRight:edadBetween 24 and 28" = "2018 * Right * Age 24-28",
  "ola4:pos_idRight:edadBetween 24 and 28" = "2019 * Right * Age 24-28",
  "ola5:pos_idRight:edadBetween 24 and 28" = "2021 * Right * Age 24-28",
  "ola6:pos_idRight:edadBetween 24 and 28" = "2022 * Right * Age 24-28",
  "ola7:pos_idRight:edadBetween 24 and 28" = "2023 * Right * Age 24-28",
  "ola2:pos_idDoesn't identify:edadBetween 24 and 28" = "2017 * Doesn't identify * Age 24-28",
  "ola3:pos_idDoesn't identify:edadBetween 24 and 28" = "2018 * Doesn't identify * Age 24-28",
  "ola4:pos_idDoesn't identify:edadBetween 24 and 28" = "2019 * Doesn't identify * Age 24-28",
  "ola5:pos_idDoesn't identify:edadBetween 24 and 28" = "2021 * Doesn't identify * Age 24-28",
  "ola6:pos_idDoesn't identify:edadBetween 24 and 28" = "2022 * Doesn't identify * Age 24-28",
  "ola7:pos_idDoesn't identify:edadBetween 24 and 28" = "2023 * Doesn't identify * Age 24-28",
  "ola2:pos_idCenter:edadBetween 18 and 23" = "2017 * Center * Age 18-23",
  "ola3:pos_idCenter:edadBetween 18 and 23" = "2018 * Center * Age 18-23",
  "ola4:pos_idCenter:edadBetween 18 and 23" = "2019 * Center * Age 18-23",
  "ola5:pos_idCenter:edadBetween 18 and 23" = "2021 * Center * Age 18-23",
  "ola6:pos_idCenter:edadBetween 18 and 23" = "2022 * Center * Age 18-23",
  "ola7:pos_idCenter:edadBetween 18 and 23" = "2023 * Center * Age 18-23",
  "ola2:pos_idRight:edadBetween 18 and 23" = "2017 * Right * Age 18-23",
  "ola3:pos_idRight:edadBetween 18 and 23" = "2018 * Right * Age 18-23",
  "ola4:pos_idRight:edadBetween 18 and 23" = "2019 * Right * Age 18-23",
  "ola5:pos_idRight:edadBetween 18 and 23" = "2021 * Right * Age 18-23",
  "ola6:pos_idRight:edadBetween 18 and 23" = "2022 * Right * Age 18-23",
  "ola7:pos_idRight:edadBetween 18 and 23" = "2023 * Right * Age 18-23",
  "ola2:pos_idDoesn't identify:edadBetween 18 and 23" = "2017 * Doesn't identify * Age 18-23",
  "ola3:pos_idDoesn't identify:edadBetween 18 and 23" = "2018 * Doesn't identify * Age 18-23",
  "ola4:pos_idDoesn't identify:edadBetween 18 and 23" = "2019 * Doesn't identify * Age 18-23",
  "ola5:pos_idDoesn't identify:edadBetween 18 and 23" = "2021 * Doesn't identify * Age 18-23",
  "ola6:pos_idDoesn't identify:edadBetween 18 and 23" = "2022 * Doesn't identify * Age 18-23",
  "ola7:pos_idDoesn't identify:edadBetween 18 and 23" = "2023 * Doesn't identify * Age 18-23",
  "educTechnical:edadBetween 29 and 45" = "Technical * Age 29-45",
  "educUniversity or more:edadBetween 29 and 45" = "University * Age 29-45",
  "educTechnical:edadBetween 24 and 28" = "Technical * Age 24-28",
  "educUniversity or more:edadBetween 24 and 28" = "University * Age 24-28",
  "educTechnical:edadBetween 18 and 23" = "Technical * Age 18-23",
  "educUniversity or more:edadBetween 18 and 23" = "University * Age 18-23",
  "ola2:educTechnical:edadBetween 29 and 45" = "2017 * Technical * Age 29-45",
  "ola3:educTechnical:edadBetween 29 and 45" = "2018 * Technical * Age 29-45",
  "ola4:educTechnical:edadBetween 29 and 45" = "2019 * Technical * Age 29-45",
  "ola5:educTechnical:edadBetween 29 and 45" = "2021 * Technical * Age 29-45",
  "ola6:educTechnical:edadBetween 29 and 45" = "2022 * Technical * Age 29-45",
  "ola7:educTechnical:edadBetween 29 and 45" = "2023 * Technical * Age 29-45",
  "ola2:educUniversity or more:edadBetween 29 and 45" = "2017 * University * Age 29-45",
  "ola3:educUniversity or more:edadBetween 29 and 45" = "2018 * University * Age 29-45",
  "ola4:educUniversity or more:edadBetween 29 and 45" = "2019 * University * Age 29-45",
  "ola5:educUniversity or more:edadBetween 29 and 45" = "2021 * University * Age 29-45",
  "ola6:educUniversity or more:edadBetween 29 and 45" = "2022 * University * Age 29-45",
  "ola7:educUniversity or more:edadBetween 29 and 45" = "2023 * University * Age 29-45",
  "ola2:educTechnical:edadBetween 24 and 28" = "2017 * Technical * Age 24-28",
  "ola3:educTechnical:edadBetween 24 and 28" = "2018 * Technical * Age 24-28",
  "ola4:educTechnical:edadBetween 24 and 28" = "2019 * Technical * Age 24-28",
  "ola5:educTechnical:edadBetween 24 and 28" = "2021 * Technical * Age 24-28",
  "ola6:educTechnical:edadBetween 24 and 28" = "2022 * Technical * Age 24-28",
  "ola7:educTechnical:edadBetween 24 and 28" = "2023 * Technical * Age 24-28",
  "ola2:educUniversity or more:edadBetween 24 and 28" = "2017 * University * Age 24-28",
  "ola3:educUniversity or more:edadBetween 24 and 28" = "2018 * University * Age 24-28",
  "ola4:educUniversity or more:edadBetween 24 and 28" = "2019 * University * Age 24-28",
  "ola5:educUniversity or more:edadBetween 24 and 28" = "2021 * University * Age 24-28",
  "ola6:educUniversity or more:edadBetween 24 and 28" = "2022 * University * Age 24-28",
  "ola7:educUniversity or more:edadBetween 24 and 28" = "2023 * University * Age 24-28",
  "ola2:educTechnical:edadBetween 18 and 23" = "2017 * Technical * Age 18-23",
  "ola3:educTechnical:edadBetween 18 and 23" = "2018 * Technical * Age 18-23",
  "ola4:educTechnical:edadBetween 18 and 23" = "2019 * Technical * Age 18-23",
  "ola5:educTechnical:edadBetween 18 and 23" = "2021 * Technical * Age 18-23",
  "ola6:educTechnical:edadBetween 18 and 23" = "2022 * Technical * Age 18-23",
  "ola7:educTechnical:edadBetween 18 and 23" = "2023 * Technical * Age 18-23",
  "ola2:educUniversity or more:edadBetween 18 and 23" = "2017 * University * Age 18-23",
  "ola3:educUniversity or more:edadBetween 18 and 23" = "2018 * University * Age 18-23",
  "ola4:educUniversity or more:edadBetween 18 and 23" = "2019 * University * Age 18-23",
  "ola5:educUniversity or more:edadBetween 18 and 23" = "2021 * University * Age 18-23",
  "ola6:educUniversity or more:edadBetween 18 and 23" = "2022 * University * Age 18-23",
  "ola7:educUniversity or more:edadBetween 18 and 23" = "2023 * University * Age 18-23",
  "sexoWoman:edadBetween 29 and 45" = "Woman * Age 29-45",
  "sexoWoman:edadBetween 29 and 45" = "Woman * Age 24-28",
  "sexoWoman:edadBetween 29 and 45" = "Woman * Age 18-23",
  "ola2:sexoWoman:edadBetween 29 and 45" = "2017 * Woman * Age 29-45",
  "ola3:sexoWoman:edadBetween 29 and 45" = "2018 * Woman * Age 29-45",
  "ola4:sexoWoman:edadBetween 29 and 45" = "2019 * Woman * Age 29-45",
  "ola5:sexoWoman:edadBetween 29 and 45" = "2021 * Woman * Age 29-45",
  "ola6:sexoWoman:edadBetween 29 and 45" = "2022 * Woman * Age 29-45",
  "ola7:sexoWoman:edadBetween 29 and 45" = "2023 * Woman * Age 29-45",
  "ola2:sexoWoman:edadBetween 24 and 28" = "2017 * Woman * Age 24-28",
  "ola3:sexoWoman:edadBetween 24 and 28" = "2018 * Woman * Age 24-28",
  "ola4:sexoWoman:edadBetween 24 and 28" = "2019 * Woman * Age 24-28",
  "ola5:sexoWoman:edadBetween 24 and 28" = "2021 * Woman * Age 24-28",
  "ola6:sexoWoman:edadBetween 24 and 28" = "2022 * Woman * Age 24-28",
  "ola7:sexoWoman:edadBetween 24 and 28" = "2023 * Woman * Age 24-28",
  "ola2:sexoWoman:edadBetween 18 and 23" = "2017 * Woman * Age 18-23",
  "ola3:sexoWoman:edadBetween 18 and 23" = "2018 * Woman * Age 18-23",
  "ola4:sexoWoman:edadBetween 18 and 23" = "2019 * Woman * Age 18-23",
  "ola5:sexoWoman:edadBetween 18 and 23" = "2021 * Woman * Age 18-23",
  "ola6:sexoWoman:edadBetween 18 and 23" = "2022 * Woman * Age 18-23",
  "ola7:sexoWoman:edadBetween 18 and 23" = "2023 * Woman * Age 18-23"
  )

texreg::knitreg(list(marchar6, marchar7, marchar8, marchar9, marchar10, marchar11,marchar12),
               custom.model.names = c(paste0("Model ", seq(6:12))),
               caption.above = T,
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef2,
               digits = 2,
               custom.note = "Note: Cells contain regression coefficients with standard errors in parentheses. \n %stars.",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.80,
               include.loglik = FALSE,
               include.aic = FALSE,
               center = T,
               custom.gof.names = c("BIC", "Numb. obs.", "Num. groups: individuals", "Var: individuals (Intercept)", "Var: Residual"))
```

### Resume table

```{r}
betas <- marchar12@beta                           # Coeficientes
vcov_mat <- as.matrix(vcov(marchar12))              # Matriz de varianzas-covarianzas
ses <- sqrt(diag(vcov_mat))                         # Errores estándar
tvals <- betas / ses                              # Valores t

ses <- ses[44:61]
betas <- betas[44:61]
tvals <- tvals[44:61]

pvals <- 2 * pnorm(-abs(tvals))  # Aproximación tipo Wald (z-score)

signif_stars <- ifelse(pvals <= 0.001, "***",
                 ifelse(pvals <= 0.01, "**",
                 ifelse(pvals <= 0.05, "*", "")))

olasexoedad<-data.frame(
  Estimate = betas,
  Signif = signif_stars
)

betas <- marchar11@beta                          # Coeficientes
vcov_mat <- as.matrix(vcov(marchar11))              # Matriz de varianzas-covarianzas
ses <- sqrt(diag(vcov_mat))                         # Errores estándar
tvals <- betas / ses                              # Valores t

ses <- ses[53:88]
betas <- betas[53:88]
tvals <- tvals[53:88]

pvals <- 2 * pnorm(-abs(tvals))  # Aproximación tipo Wald (z-score)

signif_stars <- ifelse(pvals <= 0.001, "***",
                 ifelse(pvals <= 0.01, "**",
                 ifelse(pvals <= 0.05, "*", "")))

olaeducedad<-data.frame(
  Estimate = betas,
  Signif = signif_stars
)

betas <- marchar10@beta                          # Coeficientes
vcov_mat <- as.matrix(vcov(marchar10))              # Matriz de varianzas-covarianzas
ses <- sqrt(diag(vcov_mat))                         # Errores estándar
tvals <- betas / ses                              # Valores t

ses <- ses[62:115]
betas <- betas[62:115]
tvals <- tvals[62:115]

pvals <- 2 * pnorm(-abs(tvals))  # Aproximación tipo Wald (z-score)

signif_stars <- ifelse(pvals <= 0.001, "***",
                 ifelse(pvals <= 0.01, "**",
                 ifelse(pvals <= 0.05, "*", "")))

olapospoledad<-data.frame(
  Estimate = betas,
  Signif = signif_stars
)

# Woman (olasexoedad)
woman_idx <- c(1, 7, 13, 2, 8, 14, 3, 9, 15, 4, 10, 16, 5, 11, 17, 6, 12, 18)

# Technical (olaeducedad)
technical_idx <- c(1, 13, 25, 2, 14, 26, 3, 15, 27, 4, 16, 28, 5, 17, 29, 6, 18, 30)

# University (olaeducedad)
university_idx <- c(7, 19, 31, 8, 20, 32, 9, 21, 33, 10, 22, 34, 11, 23, 35, 12, 24, 36)

# Edad 29–45 → posiciones: 1, 19, 37, 2, 20, 38, 3, 21, 39, ...
center_idx <- c(1, 19, 37, 2, 20, 38, 3, 21, 39, 4, 22, 40, 5, 23, 41, 6, 24, 42)
right_idx  <- c(7, 25, 43, 8, 26, 44, 9, 27, 45,10, 28, 46,11, 29, 47,12, 30, 48)
dni_idx    <- c(13, 31, 49,14, 32, 50,15, 33, 51,16, 34, 52,17, 35, 53,18, 36, 54)

tabla <- cbind(
  Year = c("2017", "2017", "2017", 
          "2018", "2018", "2018",
          "2019", "2019", "2019",
          "2021", "2021", "2021", 
          "2022", "2022", "2022", 
          "2023", "2023", "2023"),
  Age = rep(c("29–45", "24–28", "18–23"), times = 6),
  Woman = paste0(round(olasexoedad$Estimate[woman_idx], 2), olasexoedad$Signif[woman_idx]),
  Technical = paste0(round(olaeducedad$Estimate[technical_idx], 2), olaeducedad$Signif[technical_idx]),
  University = paste0(round(olaeducedad$Estimate[university_idx], 2), olaeducedad$Signif[university_idx]),
  Center = paste0(round(olapospoledad$Estimate[center_idx], 2), olapospoledad$Signif[center_idx]),
  Right = paste0(round(olapospoledad$Estimate[right_idx], 2), olapospoledad$Signif[right_idx]),
  `Doesnt Identify` = paste0(round(olapospoledad$Estimate[dni_idx], 2), olapospoledad$Signif[dni_idx])
)
```

```{r}
kbl(tabla, 
    align = "c") %>% 
    add_header_above(c(" " = 3,
                     "Education"=2, 
                     "Political position"=3),
                   bold = T)%>%  
  kable_paper("hover",full_width = F) %>%
     column_spec(1, bold = T) %>%
     collapse_rows(columns = 1, valign = "middle") %>% 
  footnote("***p < 0.001; **p < 0.01; *p < 0.05.")
```

## Interaction effects graphs

```{r}
waves <- c("2016", "2017", "2018", "2019", "2021", "2022", "2023")
```

- Participation online and age

```{r}
preds <- ggpredict(marchar6, terms = c("ola", "edad"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
 # facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Online participation",
    color = "Age"
  ) +
  ylim(0, 5) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Participation online and sex

```{r}
preds <- ggpredict(marchar7, terms = c("ola", "sexo"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
 # facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Online participation",
    color = "Sex"
  ) +
  ylim(0, 5) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Participation online, age and sex

```{r}
preds <- ggpredict(marchar12, terms = c("ola", "edad", "sexo"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Online participation",
    color = "Age"
  ) +
  ylim(0, 5) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Participation online and education

```{r}
preds <- ggpredict(marchar8, terms = c("ola", "educ"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
#  facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Online participation",
    color = "Education"
  ) +
  ylim(0, 5) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Participation online, age and education

```{r}
preds <- ggpredict(marchar11, terms = c("ola", "edad", "educ"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  facet_wrap(~ facet, ncol = 3) +
  labs(
    x = "Year",
    y = "Online participation",
    color = "Age"
  ) +
  ylim(0, 5) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Participation online and political position

```{r}
preds <- ggpredict(marchar9, terms = c("ola", "pos_id"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
#  facet_wrap(~ facet, ncol = 3) +
  labs(
    x = "Year",
    y = "Online participation",
    color = "Political position"
  ) +
  ylim(0, 5) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Participation online. age and political position

```{r}
preds <- ggpredict(marchar10, terms = c("ola", "edad", "pos_id"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Online participation",
    color = "edad"
  ) +
  ylim(0, 5) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```


# Participation in demonstrations

```{r}
#if (!require("pacman")) install.packedads("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg,
               interactions,
               ggplot2,
               ggeffects
               )
load(file = here::here("input/data-proc/df_study1_long_t7.RData"))

# generate analytical sample
df_study1 <- 
  df_study1_long_t7 %>%
  select(idencuesta,ola,part_marchas, edad, sexo, pos_id, educ, universitaria, ponderador_long_total) %>% 
  na.omit() %>% 
  mutate(ola_num=as.numeric(ola),
         ola=as.factor(ola),
         edad = case_when(edad <=23~"Between 18 and 23",
                          edad >23 & edad <=28 ~ "Between 24 and 28",
                          edad >28 & edad <=45 ~ "Between 29 and 45",
                          edad > 45 ~ "More than 45")) 

df_study1$edad <- factor(df_study1$edad, levels = c("More than 45", "Between 29 and 45", "Between 24 and 28", "Between 18 and 23"))
df_study1$sexo <- factor(df_study1$sexo, levels = c(1, 2), labels = c("Man", "Woman"))
df_study1$educ <- factor(df_study1$educ,
                         levels = c("Media o menos", "Técnica", "Universitaria"),
                         labels = c("Secondary or less", "Technical", "University or more"))
df_study1$pos_id <- factor(df_study1$pos_id,
                         levels = c("Izquierda", "Centro", "Derecha", "No se identifica"),
                         labels = c("Left", "Center", "Right", "Doesn't identify"))


marchar.null <- lmer(formula(paste0("part_marchas~","1 + (1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar1 <- lmer(formula(paste0("part_marchas~",h1,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar2 <- lmer(formula(paste0("part_marchas~",h2,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar3 <- lmer(formula(paste0("part_marchas~",h3,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar4 <- lmer(formula(paste0("part_marchas~",h4,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar5 <- lmer(formula(paste0("part_marchas~",h5,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar6 <- lmer(formula(paste0("part_marchas~",h6,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar7 <- lmer(formula(paste0("part_marchas~",h7,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar8 <- lmer(formula(paste0("part_marchas~",h8,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar9 <- lmer(formula(paste0("part_marchas~",h9,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar10 <- lmer(formula(paste0("part_marchas~",h10,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar11 <- lmer(formula(paste0("part_marchas~",h11,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar12 <- lmer(formula(paste0("part_marchas~",h12,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
```

## Main effects

```{r results='asis'}
ccoef <- list(
  "(Intercept)" = "Intercept",
  "ola2" = "2017",
  "ola3" = "2018",
  "ola4" = "2019",
  "ola5" = "2021",
  "ola6" = "2022",
  "ola7" = "2023",
  "edadBetween 29 and 45" = "Between 29 and 45",
  "edadBetween 24 and 28" = "Between 24 and 28",
  "edadBetween 18 and 23" = "Between 18 and 23",
  "sexoWoman" = "Woman (Ref.= Man)",
  "educTechnical" = "Technical",
  "educUniversity or more" = "University or more",
  "pos_idCenter" = "Center",
  "pos_idRight" = "Right",
  "pos_idDoesn't identify" = "Doesn't identify"
  )

texreg::knitreg(list(marchar1, marchar2, marchar3, marchar4, marchar5),
               custom.model.names = c(paste0("Model ", seq(1:5))),
               caption.above = T,
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef,
               digits = 2,
               groups = list("Wave (Ref.= 2016)" = 2:7,
                             "Age (Ref.= More than 45)" = 8:10,
                             "Education (Ref.= Secondary)" = 12:13,
                             "Political position (Ref.= Left)" = 14:16),
               custom.note = "Note: Cells contain regression coefficients with standard errors in parentheses. \n %stars.",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.80,
               include.loglik = FALSE,
               include.aic = FALSE,
               center = T,
               custom.gof.names = c("BIC", "Numb. obs.", "Num. groups: individuals", "Var: individuals (Intercept)", "Var: Residual")
               )
```

## Interaction effects

```{r results='asis'}
ccoef2 <- list(
  "(Intercept)" = "Intercept",
  "ola2:edadBetween 29 and 45" = "2017*Age 29-45",
  "ola3:edadBetween 29 and 45" = "2018*Age 29-45",
  "ola4:edadBetween 29 and 45" = "2019*Age 29-45",
  "ola5:edadBetween 29 and 45" = "2021*Age 29-45",
  "ola6:edadBetween 29 and 45" = "2022*Age 29-45",
  "ola7:edadBetween 29 and 45" = "2023*Age 29-45",
  "ola2:edadBetween 24 and 28" = "2017*Age 24-28",
  "ola3:edadBetween 24 and 28" = "2018*Age 24-28",
  "ola4:edadBetween 24 and 28" = "2019*Age 24-28",
  "ola5:edadBetween 24 and 28" = "2021*Age 24-28",
  "ola6:edadBetween 24 and 28" = "2022*Age 24-28",
  "ola7:edadBetween 24 and 28" = "2023*Age 24-28",
  "ola2:edadBetween 18 and 23" = "2017*Age 18-23",
  "ola3:edadBetween 18 and 23" = "2018*Age 18-23",
  "ola4:edadBetween 18 and 23" = "2019*Age 18-23",
  "ola5:edadBetween 18 and 23" = "2021*Age 18-23",
  "ola6:edadBetween 18 and 23" = "2022*Age 18-23",
  "ola7:edadBetween 18 and 23" = "2023*Age 18-23",
  "ola2:sexoWoman" = "2017*Woman",
  "ola3:sexoWoman" = "2018*Woman",
  "ola4:sexoWoman" = "2019*Woman",
  "ola5:sexoWoman" = "2021*Woman",
  "ola6:sexoWoman" = "2022*Woman",
  "ola7:sexoWoman" = "2023*Woman",
  "ola2:educTechnical" = "2017*Technical",
  "ola3:educTechnical" = "2018*Technical",
  "ola4:educTechnical" = "2019*Technical",
  "ola5:educTechnical" = "2021*Technical",
  "ola6:educTechnical" = "2022*Technical",
  "ola7:educTechnical" = "2023*Technical",
  "ola2:educUniversity or more" = "2017*University",
  "ola3:educUniversity or more" = "2018*University",
  "ola4:educUniversity or more" = "2019*University",
  "ola5:educUniversity or more" = "2021*University",
  "ola6:educUniversity or more" = "2022*University",
  "ola7:educUniversity or more" = "2023*University",
  "ola2:pos_idCenter" = "2017*Center",
  "ola3:pos_idCenter" = "2018*Center",
  "ola4:pos_idCenter" = "2019*Center",
  "ola5:pos_idCenter" = "2021*Center",
  "ola6:pos_idCenter" = "2022*Center",
  "ola7:pos_idCenter" = "2023*Center",
  "ola2:pos_idRight" = "2017*Right",
  "ola3:pos_idRight" = "2018*Right",
  "ola4:pos_idRight" = "2019*Right",
  "ola5:pos_idRight" = "2021*Right",
  "ola6:pos_idRight" = "2022*Right",
  "ola7:pos_idRight" = "2023*Right",
  "ola2:pos_idDoesn't identify" = "2017*Doesn't identify",
  "ola3:pos_idDoesn't identify" = "2018*Doesn't identify",
  "ola4:pos_idDoesn't identify" = "2019*Doesn't identify",
  "ola5:pos_idDoesn't identify" = "2021*Doesn't identify",
  "ola6:pos_idDoesn't identify" = "2022*Doesn't identify",
  "ola7:pos_idDoesn't identify" = "2023*Doesn't identify",
  "pos_idCenter:edadBetween 29 and 45" = "Center*Age 29-45",
  "pos_idRight:edadBetween 29 and 45" = "Right*Age 29-45",
  "pos_idDoesn't identify:edadBetween 29 and 45" = "Doesn't identify * Age 29-45",
  "pos_idCenter:edadBetween 29 and 45" = "Center*Age 24-28",
  "pos_idRight:edadBetween 29 and 45" = "Right*Age 24-28",
  "pos_idDoesn't identify:edadBetween 29 and 45" = "Doesn't identify * Age 24-28",
  "pos_idCenter:edadBetween 29 and 45" = "Center*Age 18-23",
  "pos_idRight:edadBetween 29 and 45" = "Right*Age 18-23",
  "pos_idDoesn't identify:edadBetween 29 and 45" = "Doesn't identify * Age 18-23",
  "ola2:pos_idCenter:edadBetween 29 and 45" = "2017 * Center * Age 29-45",
  "ola3:pos_idCenter:edadBetween 29 and 45" = "2018 * Center * Age 29-45",
  "ola4:pos_idCenter:edadBetween 29 and 45" = "2019 * Center * Age 29-45",
  "ola5:pos_idCenter:edadBetween 29 and 45" = "2021 * Center * Age 29-45",
  "ola6:pos_idCenter:edadBetween 29 and 45" = "2022 * Center * Age 29-45",
  "ola7:pos_idCenter:edadBetween 29 and 45" = "2023 * Center * Age 29-45",
  "ola2:pos_idRight:edadBetween 29 and 45" = "2017 * Right * Age 29-45",
  "ola3:pos_idRight:edadBetween 29 and 45" = "2018 * Right * Age 29-45",
  "ola4:pos_idRight:edadBetween 29 and 45" = "2019 * Right * Age 29-45",
  "ola5:pos_idRight:edadBetween 29 and 45" = "2021 * Right * Age 29-45",
  "ola6:pos_idRight:edadBetween 29 and 45" = "2022 * Right * Age 29-45",
  "ola7:pos_idRight:edadBetween 29 and 45" = "2023 * Right * Age 29-45",
  "ola2:pos_idDoesn't identify:edadBetween 29 and 45" = "2017 * Doesn't identify * Age 29-45",
  "ola3:pos_idDoesn't identify:edadBetween 29 and 45" = "2018 * Doesn't identify * Age 29-45",
  "ola4:pos_idDoesn't identify:edadBetween 29 and 45" = "2019 * Doesn't identify * Age 29-45",
  "ola5:pos_idDoesn't identify:edadBetween 29 and 45" = "2021 * Doesn't identify * Age 29-45",
  "ola6:pos_idDoesn't identify:edadBetween 29 and 45" = "2022 * Doesn't identify * Age 29-45",
  "ola7:pos_idDoesn't identify:edadBetween 29 and 45" = "2023 * Doesn't identify * Age 29-45",
  "ola2:pos_idCenter:edadBetween 24 and 28" = "2017 * Center * Age 24-28",
  "ola3:pos_idCenter:edadBetween 24 and 28" = "2018 * Center * Age 24-28",
  "ola4:pos_idCenter:edadBetween 24 and 28" = "2019 * Center * Age 24-28",
  "ola5:pos_idCenter:edadBetween 24 and 28" = "2021 * Center * Age 24-28",
  "ola6:pos_idCenter:edadBetween 24 and 28" = "2022 * Center * Age 24-28",
  "ola7:pos_idCenter:edadBetween 24 and 28" = "2023 * Center * Age 24-28",
  "ola2:pos_idRight:edadBetween 24 and 28" = "2017 * Right * Age 24-28",
  "ola3:pos_idRight:edadBetween 24 and 28" = "2018 * Right * Age 24-28",
  "ola4:pos_idRight:edadBetween 24 and 28" = "2019 * Right * Age 24-28",
  "ola5:pos_idRight:edadBetween 24 and 28" = "2021 * Right * Age 24-28",
  "ola6:pos_idRight:edadBetween 24 and 28" = "2022 * Right * Age 24-28",
  "ola7:pos_idRight:edadBetween 24 and 28" = "2023 * Right * Age 24-28",
  "ola2:pos_idDoesn't identify:edadBetween 24 and 28" = "2017 * Doesn't identify * Age 24-28",
  "ola3:pos_idDoesn't identify:edadBetween 24 and 28" = "2018 * Doesn't identify * Age 24-28",
  "ola4:pos_idDoesn't identify:edadBetween 24 and 28" = "2019 * Doesn't identify * Age 24-28",
  "ola5:pos_idDoesn't identify:edadBetween 24 and 28" = "2021 * Doesn't identify * Age 24-28",
  "ola6:pos_idDoesn't identify:edadBetween 24 and 28" = "2022 * Doesn't identify * Age 24-28",
  "ola7:pos_idDoesn't identify:edadBetween 24 and 28" = "2023 * Doesn't identify * Age 24-28",
  "ola2:pos_idCenter:edadBetween 18 and 23" = "2017 * Center * Age 18-23",
  "ola3:pos_idCenter:edadBetween 18 and 23" = "2018 * Center * Age 18-23",
  "ola4:pos_idCenter:edadBetween 18 and 23" = "2019 * Center * Age 18-23",
  "ola5:pos_idCenter:edadBetween 18 and 23" = "2021 * Center * Age 18-23",
  "ola6:pos_idCenter:edadBetween 18 and 23" = "2022 * Center * Age 18-23",
  "ola7:pos_idCenter:edadBetween 18 and 23" = "2023 * Center * Age 18-23",
  "ola2:pos_idRight:edadBetween 18 and 23" = "2017 * Right * Age 18-23",
  "ola3:pos_idRight:edadBetween 18 and 23" = "2018 * Right * Age 18-23",
  "ola4:pos_idRight:edadBetween 18 and 23" = "2019 * Right * Age 18-23",
  "ola5:pos_idRight:edadBetween 18 and 23" = "2021 * Right * Age 18-23",
  "ola6:pos_idRight:edadBetween 18 and 23" = "2022 * Right * Age 18-23",
  "ola7:pos_idRight:edadBetween 18 and 23" = "2023 * Right * Age 18-23",
  "ola2:pos_idDoesn't identify:edadBetween 18 and 23" = "2017 * Doesn't identify * Age 18-23",
  "ola3:pos_idDoesn't identify:edadBetween 18 and 23" = "2018 * Doesn't identify * Age 18-23",
  "ola4:pos_idDoesn't identify:edadBetween 18 and 23" = "2019 * Doesn't identify * Age 18-23",
  "ola5:pos_idDoesn't identify:edadBetween 18 and 23" = "2021 * Doesn't identify * Age 18-23",
  "ola6:pos_idDoesn't identify:edadBetween 18 and 23" = "2022 * Doesn't identify * Age 18-23",
  "ola7:pos_idDoesn't identify:edadBetween 18 and 23" = "2023 * Doesn't identify * Age 18-23",
  "educTechnical:edadBetween 29 and 45" = "Technical * Age 29-45",
  "educUniversity or more:edadBetween 29 and 45" = "University * Age 29-45",
  "educTechnical:edadBetween 24 and 28" = "Technical * Age 24-28",
  "educUniversity or more:edadBetween 24 and 28" = "University * Age 24-28",
  "educTechnical:edadBetween 18 and 23" = "Technical * Age 18-23",
  "educUniversity or more:edadBetween 18 and 23" = "University * Age 18-23",
  "ola2:educTechnical:edadBetween 29 and 45" = "2017 * Technical * Age 29-45",
  "ola3:educTechnical:edadBetween 29 and 45" = "2018 * Technical * Age 29-45",
  "ola4:educTechnical:edadBetween 29 and 45" = "2019 * Technical * Age 29-45",
  "ola5:educTechnical:edadBetween 29 and 45" = "2021 * Technical * Age 29-45",
  "ola6:educTechnical:edadBetween 29 and 45" = "2022 * Technical * Age 29-45",
  "ola7:educTechnical:edadBetween 29 and 45" = "2023 * Technical * Age 29-45",
  "ola2:educUniversity or more:edadBetween 29 and 45" = "2017 * University * Age 29-45",
  "ola3:educUniversity or more:edadBetween 29 and 45" = "2018 * University * Age 29-45",
  "ola4:educUniversity or more:edadBetween 29 and 45" = "2019 * University * Age 29-45",
  "ola5:educUniversity or more:edadBetween 29 and 45" = "2021 * University * Age 29-45",
  "ola6:educUniversity or more:edadBetween 29 and 45" = "2022 * University * Age 29-45",
  "ola7:educUniversity or more:edadBetween 29 and 45" = "2023 * University * Age 29-45",
  "ola2:educTechnical:edadBetween 24 and 28" = "2017 * Technical * Age 24-28",
  "ola3:educTechnical:edadBetween 24 and 28" = "2018 * Technical * Age 24-28",
  "ola4:educTechnical:edadBetween 24 and 28" = "2019 * Technical * Age 24-28",
  "ola5:educTechnical:edadBetween 24 and 28" = "2021 * Technical * Age 24-28",
  "ola6:educTechnical:edadBetween 24 and 28" = "2022 * Technical * Age 24-28",
  "ola7:educTechnical:edadBetween 24 and 28" = "2023 * Technical * Age 24-28",
  "ola2:educUniversity or more:edadBetween 24 and 28" = "2017 * University * Age 24-28",
  "ola3:educUniversity or more:edadBetween 24 and 28" = "2018 * University * Age 24-28",
  "ola4:educUniversity or more:edadBetween 24 and 28" = "2019 * University * Age 24-28",
  "ola5:educUniversity or more:edadBetween 24 and 28" = "2021 * University * Age 24-28",
  "ola6:educUniversity or more:edadBetween 24 and 28" = "2022 * University * Age 24-28",
  "ola7:educUniversity or more:edadBetween 24 and 28" = "2023 * University * Age 24-28",
  "ola2:educTechnical:edadBetween 18 and 23" = "2017 * Technical * Age 18-23",
  "ola3:educTechnical:edadBetween 18 and 23" = "2018 * Technical * Age 18-23",
  "ola4:educTechnical:edadBetween 18 and 23" = "2019 * Technical * Age 18-23",
  "ola5:educTechnical:edadBetween 18 and 23" = "2021 * Technical * Age 18-23",
  "ola6:educTechnical:edadBetween 18 and 23" = "2022 * Technical * Age 18-23",
  "ola7:educTechnical:edadBetween 18 and 23" = "2023 * Technical * Age 18-23",
  "ola2:educUniversity or more:edadBetween 18 and 23" = "2017 * University * Age 18-23",
  "ola3:educUniversity or more:edadBetween 18 and 23" = "2018 * University * Age 18-23",
  "ola4:educUniversity or more:edadBetween 18 and 23" = "2019 * University * Age 18-23",
  "ola5:educUniversity or more:edadBetween 18 and 23" = "2021 * University * Age 18-23",
  "ola6:educUniversity or more:edadBetween 18 and 23" = "2022 * University * Age 18-23",
  "ola7:educUniversity or more:edadBetween 18 and 23" = "2023 * University * Age 18-23",
  "sexoWoman:edadBetween 29 and 45" = "Woman * Age 29-45",
  "sexoWoman:edadBetween 24 and 28" = "Woman * Age 24-28",
  "sexoWoman:edadBetween 18 and 23" = "Woman * Age 18-23",
  "ola2:sexoWoman:edadBetween 29 and 45" = "2017 * Woman * Age 29-45",
  "ola3:sexoWoman:edadBetween 29 and 45" = "2018 * Woman * Age 29-45",
  "ola4:sexoWoman:edadBetween 29 and 45" = "2019 * Woman * Age 29-45",
  "ola5:sexoWoman:edadBetween 29 and 45" = "2021 * Woman * Age 29-45",
  "ola6:sexoWoman:edadBetween 29 and 45" = "2022 * Woman * Age 29-45",
  "ola7:sexoWoman:edadBetween 29 and 45" = "2023 * Woman * Age 29-45",
  "ola2:sexoWoman:edadBetween 24 and 28" = "2017 * Woman * Age 24-28",
  "ola3:sexoWoman:edadBetween 24 and 28" = "2018 * Woman * Age 24-28",
  "ola4:sexoWoman:edadBetween 24 and 28" = "2019 * Woman * Age 24-28",
  "ola5:sexoWoman:edadBetween 24 and 28" = "2021 * Woman * Age 24-28",
  "ola6:sexoWoman:edadBetween 24 and 28" = "2022 * Woman * Age 24-28",
  "ola7:sexoWoman:edadBetween 24 and 28" = "2023 * Woman * Age 24-28",
  "ola2:sexoWoman:edadBetween 18 and 23" = "2017 * Woman * Age 18-23",
  "ola3:sexoWoman:edadBetween 18 and 23" = "2018 * Woman * Age 18-23",
  "ola4:sexoWoman:edadBetween 18 and 23" = "2019 * Woman * Age 18-23",
  "ola5:sexoWoman:edadBetween 18 and 23" = "2021 * Woman * Age 18-23",
  "ola6:sexoWoman:edadBetween 18 and 23" = "2022 * Woman * Age 18-23",
  "ola7:sexoWoman:edadBetween 18 and 23" = "2023 * Woman * Age 18-23"
  )

texreg::knitreg(list(marchar6, marchar7, marchar8, marchar9, marchar10, marchar11,marchar12),
               custom.model.names = c(paste0("Model ", seq(6:12))),
               caption.above = T,
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef2,
               digits = 2,
               custom.note = "Note: Cells contain regression coefficients with standard errors in parentheses. \n %stars.",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.80,
               include.loglik = FALSE,
               include.aic = FALSE,
               center = T,
               custom.gof.names = c("BIC", "Numb. obs.", "Num. groups: individuals", "Var: individuals (Intercept)", "Var: Residual"))
```

### Resume table

```{r}
betas <- marchar12@beta                           # Coeficientes
vcov_mat <- as.matrix(vcov(marchar12))              # Matriz de varianzas-covarianzas
ses <- sqrt(diag(vcov_mat))                         # Errores estándar
tvals <- betas / ses                              # Valores t

ses <- ses[44:61]
betas <- betas[44:61]
tvals <- tvals[44:61]

pvals <- 2 * pnorm(-abs(tvals))  # Aproximación tipo Wald (z-score)

signif_stars <- ifelse(pvals <= 0.001, "***",
                 ifelse(pvals <= 0.01, "**",
                 ifelse(pvals <= 0.05, "*", "")))

olasexoedad<-data.frame(
  Estimate = betas,
  Signif = signif_stars
)


betas <- marchar11@beta                          # Coeficientes
vcov_mat <- as.matrix(vcov(marchar11))              # Matriz de varianzas-covarianzas
ses <- sqrt(diag(vcov_mat))                         # Errores estándar
tvals <- betas / ses                              # Valores t

ses <- ses[53:88]
betas <- betas[53:88]
tvals <- tvals[53:88]

pvals <- 2 * pnorm(-abs(tvals))  # Aproximación tipo Wald (z-score)

signif_stars <- ifelse(pvals <= 0.001, "***",
                 ifelse(pvals <= 0.01, "**",
                 ifelse(pvals <= 0.05, "*", "")))

olaeducedad<-data.frame(
  Estimate = betas,
  Signif = signif_stars
)


betas <- marchar10@beta                          # Coeficientes
vcov_mat <- as.matrix(vcov(marchar10))              # Matriz de varianzas-covarianzas
ses <- sqrt(diag(vcov_mat))                         # Errores estándar
tvals <- betas / ses                              # Valores t

ses <- ses[62:115]
betas <- betas[62:115]
tvals <- tvals[62:115]

pvals <- 2 * pnorm(-abs(tvals))  # Aproximación tipo Wald (z-score)

signif_stars <- ifelse(pvals <= 0.001, "***",
                 ifelse(pvals <= 0.01, "**",
                 ifelse(pvals <= 0.05, "*", "")))

olapospoledad<-data.frame(
  Estimate = betas,
  Signif = signif_stars
)

# Woman (olasexoedad)
woman_idx <- c(1, 7, 13, 2, 8, 14, 3, 9, 15, 4, 10, 16, 5, 11, 17, 6, 12, 18)

# Technical (olaeducedad)
technical_idx <- c(1, 13, 25, 2, 14, 26, 3, 15, 27, 4, 16, 28, 5, 17, 29, 6, 18, 30)

# University (olaeducedad)
university_idx <- c(7, 19, 31, 8, 20, 32, 9, 21, 33, 10, 22, 34, 11, 23, 35, 12, 24, 36)

# Edad 29–45 → posiciones: 1, 19, 37, 2, 20, 38, 3, 21, 39, ...
center_idx <- c(1, 19, 37, 2, 20, 38, 3, 21, 39, 4, 22, 40, 5, 23, 41, 6, 24, 42)
right_idx  <- c(7, 25, 43, 8, 26, 44, 9, 27, 45,10, 28, 46,11, 29, 47,12, 30, 48)
dni_idx    <- c(13, 31, 49,14, 32, 50,15, 33, 51,16, 34, 52,17, 35, 53,18, 36, 54)

tabla <- cbind(
  Year = c("2017", "2017", "2017", 
          "2018", "2018", "2018",
          "2019", "2019", "2019",
          "2021", "2021", "2021", 
          "2022", "2022", "2022", 
          "2023", "2023", "2023"),
  Age = rep(c("29–45", "24–28", "18–23"), times = 6),
  Woman = paste0(round(olasexoedad$Estimate[woman_idx], 2), olasexoedad$Signif[woman_idx]),
  Technical = paste0(round(olaeducedad$Estimate[technical_idx], 2), olaeducedad$Signif[technical_idx]),
  University = paste0(round(olaeducedad$Estimate[university_idx], 2), olaeducedad$Signif[university_idx]),
  Center = paste0(round(olapospoledad$Estimate[center_idx], 2), olapospoledad$Signif[center_idx]),
  Right = paste0(round(olapospoledad$Estimate[right_idx], 2), olapospoledad$Signif[right_idx]),
  `Doesnt Identify` = paste0(round(olapospoledad$Estimate[dni_idx], 2), olapospoledad$Signif[dni_idx])
)
```

```{r}
kbl(tabla, 
    align = "c") %>% 
    add_header_above(c(" " = 3,
                     "Education"=2, 
                     "Political position"=3),
                   bold = T)%>%  
  kable_paper("hover",full_width = F) %>%
     column_spec(1, bold = T) %>%
     collapse_rows(columns = 1, valign = "middle") %>% 
  footnote("***p < 0.001; **p < 0.01; *p < 0.05.")
```

## Interaction effects graphs

```{r}
waves <- c("2016", "2017", "2018", "2019", "2021", "2022", "2023")
```

- Participation in demonstrations and age

```{r}
preds <- ggpredict(marchar6, terms = c("ola", "edad"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
 # facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Attending marches-demonstrations",
    color = "Age"
  ) +
  ylim(0, 5) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Participation in demonstrations and sex

```{r}
preds <- ggpredict(marchar7, terms = c("ola", "sexo"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
 # facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Attending marches-demonstrations",
    color = "Sex"
  ) +
  ylim(0, 5) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Participation in demonstrations, age and sex

```{r}
preds <- ggpredict(marchar12, terms = c("ola", "edad", "sexo"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Attending marches-demonstrations",
    color = "Age"
  ) +
  ylim(0, 5) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Participation in demonstrations and education

```{r}
preds <- ggpredict(marchar8, terms = c("ola", "educ"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
#  facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Attending marches-demonstrations",
    color = "Education"
  ) +
  ylim(0, 5) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")

```

- Participation in demonstrations, age and education

```{r}
preds <- ggpredict(marchar11, terms = c("ola", "edad", "educ"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  facet_wrap(~ facet, ncol = 3) +
  labs(
    x = "Year",
    y = "Attending marches-demonstrations",
    color = "Age"
  ) +
  ylim(0, 5) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Participation in demonstrations and political position

```{r}
preds <- ggpredict(marchar9, terms = c("ola", "pos_id"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
#  facet_wrap(~ facet, ncol = 3) +
  labs(
    x = "Year",
    y = "Attending marches-demonstrations",
    color = "Political position"
  ) +
  ylim(0, 5) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")

```

- Participation in demonstrations, age and political position

```{r}
preds <- ggpredict(marchar10, terms = c("ola", "edad", "pos_id"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Attending marches-demonstrations",
    color = "Age"
  ) +
  ylim(0, 5) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")

```

# Support to same-sex adoption

```{r}
#if (!require("pacman")) install.packedads("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg
               )
load(file = here::here("input/data-proc/df_study1_long_t7.RData"))

# generate analytical sample
df_study1 <- 
  df_study1_long_t7 %>%
  select(idencuesta,ola,adop_homo, edad, sexo, pos_id, educ, universitaria, ponderador_long_total) %>% 
  na.omit() %>% 
  mutate(ola_num=as.numeric(ola),
         ola=as.factor(ola),
         edad = case_when(edad <=23~"Between 18 and 23",
                          edad >23 & edad <=28 ~ "Between 24 and 28",
                          edad >28 & edad <=45 ~ "Between 29 and 45",
                          edad > 45 ~ "More than 45")) 

df_study1$edad <- factor(df_study1$edad, levels = c("More than 45", "Between 29 and 45", "Between 24 and 28", "Between 18 and 23"))
df_study1$sexo <- factor(df_study1$sexo, levels = c(1, 2), labels = c("Man", "Woman"))
df_study1$educ <- factor(df_study1$educ,
                         levels = c("Media o menos", "Técnica", "Universitaria"),
                         labels = c("Secondary or less", "Technical", "University or more"))
df_study1$pos_id <- factor(df_study1$pos_id,
                         levels = c("Izquierda", "Centro", "Derecha", "No se identifica"),
                         labels = c("Left", "Center", "Right", "Doesn't identify"))

marchar.null <- lmer(formula(paste0("adop_homo~","1 + (1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar1 <- lmer(formula(paste0("adop_homo~",h1,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar2 <- lmer(formula(paste0("adop_homo~",h2,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar3 <- lmer(formula(paste0("adop_homo~",h3,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar4 <- lmer(formula(paste0("adop_homo~",h4,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar5 <- lmer(formula(paste0("adop_homo~",h5,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar6 <- lmer(formula(paste0("adop_homo~",h6,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar7 <- lmer(formula(paste0("adop_homo~",h7,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar8 <- lmer(formula(paste0("adop_homo~",h8,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar9 <- lmer(formula(paste0("adop_homo~",h9,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar10 <- lmer(formula(paste0("adop_homo~",h10,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar11 <- lmer(formula(paste0("adop_homo~",h11,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar12 <- lmer(formula(paste0("adop_homo~",h12,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
```

## Main effects

```{r results='asis'}
ccoef <- list(
  "(Intercept)" = "Intercept",
  "ola4" = "2019",
  "ola5" = "2021",
  "ola6" = "2022",
  "ola7" = "2023",
  "edadBetween 29 and 45" = "Between 29 and 45",
  "edadBetween 24 and 28" = "Between 24 and 28",
  "edadBetween 18 and 23" = "Between 18 and 23",
  "sexoWoman" = "Woman (Ref.= Man)",
  "educTechnical" = "Technical",
  "educUniversity or more" = "University or more",
  "pos_idCenter" = "Center",
  "pos_idRight" = "Right",
  "pos_idDoesn't identify" = "Doesn't identify"
  )

texreg::knitreg(list(marchar1, marchar2, marchar3, marchar4, marchar5),
               custom.model.names = c(paste0("Model ", seq(1:5))),
               caption.above = T,
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef,
               digits = 2,
               groups = list("Wave (Ref.= 2018)" = 2:5,
                             "Age (Ref.= More than 45)" = 6:8,
                             "Education (Ref.= Secondary)" = 10:11,
                             "Political position (Ref.= Left)" = 12:14),
               custom.note = "Note: Cells contain regression coefficients with standard errors in parentheses. \n %stars.",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.80,
               include.loglik = FALSE,
               include.aic = FALSE,
               center = T,
               custom.gof.names = c("BIC", "Numb. obs.", "Num. groups: individuals", "Var: individuals (Intercept)", "Var: Residual")
               )
```

## Interaction effects 

```{r results='asis'}
ccoef2 <- list(
  "(Intercept)" = "Intercept",
  "ola4:edadBetween 29 and 45" = "2019*Age 29-45",
  "ola5:edadBetween 29 and 45" = "2021*Age 29-45",
  "ola6:edadBetween 29 and 45" = "2022*Age 29-45",
  "ola7:edadBetween 29 and 45" = "2023*Age 29-45",
  "ola4:edadBetween 24 and 28" = "2019*Age 24-28",
  "ola5:edadBetween 24 and 28" = "2021*Age 24-28",
  "ola6:edadBetween 24 and 28" = "2022*Age 24-28",
  "ola7:edadBetween 24 and 28" = "2023*Age 24-28",
  "ola4:edadBetween 18 and 23" = "2019*Age 18-23",
  "ola5:edadBetween 18 and 23" = "2021*Age 18-23",
  "ola6:edadBetween 18 and 23" = "2022*Age 18-23",
  "ola7:edadBetween 18 and 23" = "2023*Age 18-23",
  "ola4:sexoWoman" = "2019*Woman",
  "ola5:sexoWoman" = "2021*Woman",
  "ola6:sexoWoman" = "2022*Woman",
  "ola7:sexoWoman" = "2023*Woman",
  "ola4:educTechnical" = "2019*Technical",
  "ola5:educTechnical" = "2021*Technical",
  "ola6:educTechnical" = "2022*Technical",
  "ola7:educTechnical" = "2023*Technical",
  "ola4:educUniversity or more" = "2019*University",
  "ola5:educUniversity or more" = "2021*University",
  "ola6:educUniversity or more" = "2022*University",
  "ola7:educUniversity or more" = "2023*University",
  "ola4:pos_idCenter" = "2019*Center",
  "ola5:pos_idCenter" = "2021*Center",
  "ola6:pos_idCenter" = "2022*Center",
  "ola7:pos_idCenter" = "2023*Center",
  "ola4:pos_idRight" = "2019*Right",
  "ola5:pos_idRight" = "2021*Right",
  "ola6:pos_idRight" = "2022*Right",
  "ola7:pos_idRight" = "2023*Right",
  "ola4:pos_idDoesn't identify" = "2019*Doesn't identify",
  "ola5:pos_idDoesn't identify" = "2021*Doesn't identify",
  "ola6:pos_idDoesn't identify" = "2022*Doesn't identify",
  "ola7:pos_idDoesn't identify" = "2023*Doesn't identify",
  "pos_idCenter:edadBetween 29 and 45" = "Center*Age 29-45",
  "pos_idRight:edadBetween 29 and 45" = "Right*Age 29-45",
  "pos_idDoesn't identify:edadBetween 29 and 45" = "Doesn't identify * Age 29-45",
  "pos_idCenter:edadBetween 29 and 45" = "Center*Age 24-28",
  "pos_idRight:edadBetween 29 and 45" = "Right*Age 24-28",
  "pos_idDoesn't identify:edadBetween 29 and 45" = "Doesn't identify * Age 24-28",
  "pos_idCenter:edadBetween 29 and 45" = "Center*Age 18-23",
  "pos_idRight:edadBetween 29 and 45" = "Right*Age 18-23",
  "pos_idDoesn't identify:edadBetween 29 and 45" = "Doesn't identify * Age 18-23",
  "ola4:pos_idCenter:edadBetween 29 and 45" = "2019 * Center * Age 29-45",
  "ola5:pos_idCenter:edadBetween 29 and 45" = "2021 * Center * Age 29-45",
  "ola6:pos_idCenter:edadBetween 29 and 45" = "2022 * Center * Age 29-45",
  "ola7:pos_idCenter:edadBetween 29 and 45" = "2023 * Center * Age 29-45",
  "ola4:pos_idRight:edadBetween 29 and 45" = "2019 * Right * Age 29-45",
  "ola5:pos_idRight:edadBetween 29 and 45" = "2021 * Right * Age 29-45",
  "ola6:pos_idRight:edadBetween 29 and 45" = "2022 * Right * Age 29-45",
  "ola7:pos_idRight:edadBetween 29 and 45" = "2023 * Right * Age 29-45",
  "ola4:pos_idDoesn't identify:edadBetween 29 and 45" = "2019 * Doesn't identify * Age 29-45",
  "ola5:pos_idDoesn't identify:edadBetween 29 and 45" = "2021 * Doesn't identify * Age 29-45",
  "ola6:pos_idDoesn't identify:edadBetween 29 and 45" = "2022 * Doesn't identify * Age 29-45",
  "ola7:pos_idDoesn't identify:edadBetween 29 and 45" = "2023 * Doesn't identify * Age 29-45",
  "ola4:pos_idCenter:edadBetween 24 and 28" = "2019 * Center * Age 24-28",
  "ola5:pos_idCenter:edadBetween 24 and 28" = "2021 * Center * Age 24-28",
  "ola6:pos_idCenter:edadBetween 24 and 28" = "2022 * Center * Age 24-28",
  "ola7:pos_idCenter:edadBetween 24 and 28" = "2023 * Center * Age 24-28",
  "ola4:pos_idRight:edadBetween 24 and 28" = "2019 * Right * Age 24-28",
  "ola5:pos_idRight:edadBetween 24 and 28" = "2021 * Right * Age 24-28",
  "ola6:pos_idRight:edadBetween 24 and 28" = "2022 * Right * Age 24-28",
  "ola7:pos_idRight:edadBetween 24 and 28" = "2023 * Right * Age 24-28",
  "ola4:pos_idDoesn't identify:edadBetween 24 and 28" = "2019 * Doesn't identify * Age 24-28",
  "ola5:pos_idDoesn't identify:edadBetween 24 and 28" = "2021 * Doesn't identify * Age 24-28",
  "ola6:pos_idDoesn't identify:edadBetween 24 and 28" = "2022 * Doesn't identify * Age 24-28",
  "ola7:pos_idDoesn't identify:edadBetween 24 and 28" = "2023 * Doesn't identify * Age 24-28",
  "ola4:pos_idCenter:edadBetween 18 and 23" = "2019 * Center * Age 18-23",
  "ola5:pos_idCenter:edadBetween 18 and 23" = "2021 * Center * Age 18-23",
  "ola6:pos_idCenter:edadBetween 18 and 23" = "2022 * Center * Age 18-23",
  "ola7:pos_idCenter:edadBetween 18 and 23" = "2023 * Center * Age 18-23",
  "ola4:pos_idRight:edadBetween 18 and 23" = "2019 * Right * Age 18-23",
  "ola5:pos_idRight:edadBetween 18 and 23" = "2021 * Right * Age 18-23",
  "ola6:pos_idRight:edadBetween 18 and 23" = "2022 * Right * Age 18-23",
  "ola7:pos_idRight:edadBetween 18 and 23" = "2023 * Right * Age 18-23",
  "ola4:pos_idDoesn't identify:edadBetween 18 and 23" = "2019 * Doesn't identify * Age 18-23",
  "ola5:pos_idDoesn't identify:edadBetween 18 and 23" = "2021 * Doesn't identify * Age 18-23",
  "ola6:pos_idDoesn't identify:edadBetween 18 and 23" = "2022 * Doesn't identify * Age 18-23",
  "ola7:pos_idDoesn't identify:edadBetween 18 and 23" = "2023 * Doesn't identify * Age 18-23",
  "educTechnical:edadBetween 29 and 45" = "Technical * Age 29-45",
  "educUniversity or more:edadBetween 29 and 45" = "University * Age 29-45",
  "educTechnical:edadBetween 24 and 28" = "Technical * Age 24-28",
  "educUniversity or more:edadBetween 24 and 28" = "University * Age 24-28",
  "educTechnical:edadBetween 18 and 23" = "Technical * Age 18-23",
  "educUniversity or more:edadBetween 18 and 23" = "University * Age 18-23",
  "ola4:educTechnical:edadBetween 29 and 45" = "2019 * Technical * Age 29-45",
  "ola5:educTechnical:edadBetween 29 and 45" = "2021 * Technical * Age 29-45",
  "ola6:educTechnical:edadBetween 29 and 45" = "2022 * Technical * Age 29-45",
  "ola7:educTechnical:edadBetween 29 and 45" = "2023 * Technical * Age 29-45",
  "ola4:educUniversity or more:edadBetween 29 and 45" = "2019 * University * Age 29-45",
  "ola5:educUniversity or more:edadBetween 29 and 45" = "2021 * University * Age 29-45",
  "ola6:educUniversity or more:edadBetween 29 and 45" = "2022 * University * Age 29-45",
  "ola7:educUniversity or more:edadBetween 29 and 45" = "2023 * University * Age 29-45",
  "ola4:educTechnical:edadBetween 24 and 28" = "2019 * Technical * Age 24-28",
  "ola5:educTechnical:edadBetween 24 and 28" = "2021 * Technical * Age 24-28",
  "ola6:educTechnical:edadBetween 24 and 28" = "2022 * Technical * Age 24-28",
  "ola7:educTechnical:edadBetween 24 and 28" = "2023 * Technical * Age 24-28",
  "ola4:educUniversity or more:edadBetween 24 and 28" = "2019 * University * Age 24-28",
  "ola5:educUniversity or more:edadBetween 24 and 28" = "2021 * University * Age 24-28",
  "ola6:educUniversity or more:edadBetween 24 and 28" = "2022 * University * Age 24-28",
  "ola7:educUniversity or more:edadBetween 24 and 28" = "2023 * University * Age 24-28",
  "ola4:educTechnical:edadBetween 18 and 23" = "2019 * Technical * Age 18-23",
  "ola5:educTechnical:edadBetween 18 and 23" = "2021 * Technical * Age 18-23",
  "ola6:educTechnical:edadBetween 18 and 23" = "2022 * Technical * Age 18-23",
  "ola7:educTechnical:edadBetween 18 and 23" = "2023 * Technical * Age 18-23",
  "ola4:educUniversity or more:edadBetween 18 and 23" = "2019 * University * Age 18-23",
  "ola5:educUniversity or more:edadBetween 18 and 23" = "2021 * University * Age 18-23",
  "ola6:educUniversity or more:edadBetween 18 and 23" = "2022 * University * Age 18-23",
  "ola7:educUniversity or more:edadBetween 18 and 23" = "2023 * University * Age 18-23",
  "sexoWoman:edadBetween 29 and 45" = "Woman * Age 29-45",
  "sexoWoman:edadBetween 29 and 45" = "Woman * Age 24-28",
  "sexoWoman:edadBetween 29 and 45" = "Woman * Age 18-23",
  "ola4:sexoWoman:edadBetween 29 and 45" = "2019 * Woman * Age 29-45",
  "ola5:sexoWoman:edadBetween 29 and 45" = "2021 * Woman * Age 29-45",
  "ola6:sexoWoman:edadBetween 29 and 45" = "2022 * Woman * Age 29-45",
  "ola7:sexoWoman:edadBetween 29 and 45" = "2023 * Woman * Age 29-45",
  "ola4:sexoWoman:edadBetween 24 and 28" = "2019 * Woman * Age 24-28",
  "ola5:sexoWoman:edadBetween 24 and 28" = "2021 * Woman * Age 24-28",
  "ola6:sexoWoman:edadBetween 24 and 28" = "2022 * Woman * Age 24-28",
  "ola7:sexoWoman:edadBetween 24 and 28" = "2023 * Woman * Age 24-28",
  "ola4:sexoWoman:edadBetween 18 and 23" = "2019 * Woman * Age 18-23",
  "ola5:sexoWoman:edadBetween 18 and 23" = "2021 * Woman * Age 18-23",
  "ola6:sexoWoman:edadBetween 18 and 23" = "2022 * Woman * Age 18-23",
  "ola7:sexoWoman:edadBetween 18 and 23" = "2023 * Woman * Age 18-23"
  )

texreg::knitreg(list(marchar6, marchar7, marchar8, marchar9, marchar10, marchar11,marchar12),
               custom.model.names = c(paste0("Model ", seq(6:12))),
               caption.above = T,
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef2,
               digits = 2,
               custom.note = "Note: Cells contain regression coefficients with standard errors in parentheses. \n %stars.",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.80,
               include.loglik = FALSE,
               include.aic = FALSE,
               center = T,
               custom.gof.names = c("BIC", "Numb. obs.", "Num. groups: individuals", "Var: individuals (Intercept)", "Var: Residual"))
```

### Resume table

```{r}
betas <- marchar12@beta                           # Coeficientes
vcov_mat <- as.matrix(vcov(marchar12))              # Matriz de varianzas-covarianzas
ses <- sqrt(diag(vcov_mat))                         # Errores estándar
tvals <- betas / ses                              # Valores t

ses <- ses[34:45]
betas <- betas[34:45]
tvals <- tvals[34:45]

pvals <- 2 * pnorm(-abs(tvals))  # Aproximación tipo Wald (z-score)

signif_stars <- ifelse(pvals <= 0.001, "***",
                 ifelse(pvals <= 0.01, "**",
                 ifelse(pvals <= 0.05, "*", "")))

olasexoedad<-data.frame(
  Estimate = betas,
  Signif = signif_stars
)

betas <- marchar11@beta                          # Coeficientes
vcov_mat <- as.matrix(vcov(marchar11))              # Matriz de varianzas-covarianzas
ses <- sqrt(diag(vcov_mat))                         # Errores estándar
tvals <- betas / ses                              # Valores t

ses <- ses[41:64]
betas <- betas[41:64]
tvals <- tvals[41:64]

pvals <- 2 * pnorm(-abs(tvals))  # Aproximación tipo Wald (z-score)

signif_stars <- ifelse(pvals <= 0.001, "***",
                 ifelse(pvals <= 0.01, "**",
                 ifelse(pvals <= 0.05, "*", "")))

olaeducedad<-data.frame(
  Estimate = betas,
  Signif = signif_stars
)

betas <- marchar10@beta                          # Coeficientes
vcov_mat <- as.matrix(vcov(marchar10))              # Matriz de varianzas-covarianzas
ses <- sqrt(diag(vcov_mat))                         # Errores estándar
tvals <- betas / ses                              # Valores t

ses <- ses[48:83]
betas <- betas[48:83]
tvals <- tvals[48:83]

pvals <- 2 * pnorm(-abs(tvals))  # Aproximación tipo Wald (z-score)

signif_stars <- ifelse(pvals <= 0.001, "***",
                 ifelse(pvals <= 0.01, "**",
                 ifelse(pvals <= 0.05, "*", "")))

olapospoledad<-data.frame(
  Estimate = betas,
  Signif = signif_stars
)

# Woman (olasexoedad) – 12 términos
woman_idx <- c(1, 5, 9,   # 29–45
               2, 6,10,   # 24–28
               3, 7,11,   # 18–23
               4, 8,12)   # orden por ola: 2019, 2021, 2022, 2023

# Technical (olaeducedad) – 24 términos
technical_idx <- c(1, 9,17,  # 29–45
                   2,10,18,  # 24–28
                   3,11,19,  # 18–23
                   4,12,20)  # ola 2021
# university ocupa las posiciones 5:8, 13:16, 21:24
university_idx <- c(5,13,21,  # 29–45
                    6,14,22,  # 24–28
                    7,15,23,  # 18–23
                    8,16,24)

# Center (olapospoledad) – 36 términos
center_idx <- c(1,13,25,  # 29–45
                2,14,26,  # 24–28
                3,15,27,  # 18–23
                4,16,28)  # ola 2021
right_idx <-  c(5,17,29,  # 29–45
                6,18,30,
                7,19,31,
                8,20,32)
dni_idx   <-  c(9,21,33,
                10,22,34,
                11,23,35,
                12,24,36)

tabla <- cbind(
  Year = c("2019", "2019", "2019",
          "2021", "2021", "2021", 
          "2022", "2022", "2022", 
          "2023", "2023", "2023"),
  Age = rep(c("29–45", "24–28", "18–23"), times = 4),
  Woman = paste0(round(olasexoedad$Estimate[woman_idx], 2), olasexoedad$Signif[woman_idx]),
  Technical = paste0(round(olaeducedad$Estimate[technical_idx], 2), olaeducedad$Signif[technical_idx]),
  University = paste0(round(olaeducedad$Estimate[university_idx], 2), olaeducedad$Signif[university_idx]),
  Center = paste0(round(olapospoledad$Estimate[center_idx], 2), olapospoledad$Signif[center_idx]),
  Right = paste0(round(olapospoledad$Estimate[right_idx], 2), olapospoledad$Signif[right_idx]),
  `Doesnt Identify` = paste0(round(olapospoledad$Estimate[dni_idx], 2), olapospoledad$Signif[dni_idx])
)
```

```{r}
kbl(tabla, 
    align = "c") %>% 
    add_header_above(c(" " = 3,
                     "Education"=2, 
                     "Political position"=3),
                   bold = T)%>%  
  kable_paper("hover",full_width = F) %>%
     column_spec(1, bold = T) %>%
     collapse_rows(columns = 1, valign = "middle") %>% 
  footnote("***p < 0.001; **p < 0.01; *p < 0.05.")
```

## Interaction effects graphs

- Support to same-sex adoption and age

```{r}
waves3 <- c("2018", "2019", "2021", "2022", "2023")
preds <- ggpredict(marchar6, terms = c("ola", "edad"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
 # facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Support for same-sex adoption",
    color = "Age"
  ) +
  ylim(1, 5) +
  scale_x_discrete(labels = waves3) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Support to same-sex adoption and sex

```{r}
preds <- ggpredict(marchar7, terms = c("ola", "sexo"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
 # facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Support for same-sex adoption",
    color = "Sex"
  ) +
  ylim(1, 5) +
  scale_x_discrete(labels = waves3) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Support to same-sex adoption, age and sex

```{r}
preds <- ggpredict(marchar12, terms = c("ola", "edad", "sexo"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Support for same-sex adoption",
    color = "Age"
  ) +
  ylim(1, 5) +
  scale_x_discrete(labels = waves3) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Support to same-sex adoption and education

```{r}
preds <- ggpredict(marchar8, terms = c("ola", "educ"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
#  facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Support for same-sex adoption",
    color = "Education"
  ) +
  ylim(1, 5) +
  scale_x_discrete(labels = waves3) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Support to same-sex adoption, age and education

```{r}
preds <- ggpredict(marchar11, terms = c("ola", "edad", "educ"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  facet_wrap(~ facet, ncol = 3) +
  labs(
    x = "Year",
    y = "Support for same-sex adoption",
    color = "Age"
  ) +
  ylim(1, 5) +
  scale_x_discrete(labels = waves3) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Support to same-sex adoption and political position

```{r}
preds <- ggpredict(marchar9, terms = c("ola", "pos_id"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
#  facet_wrap(~ facet, ncol = 3) +
  labs(
    x = "Year",
    y = "Support for same-sex adoption",
    color = "Political position"
  ) +
  ylim(1, 5) +
  scale_x_discrete(labels = waves3) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Support to same-sex adoption, age and political position

```{r}
preds <- ggpredict(marchar10, terms = c("ola", "edad", "pos_id"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Support for same-sex adoption",
    color = "edad"
  ) +
  ylim(1, 5) +
  scale_x_discrete(labels = waves3) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

# Support for abortion decriminalization

```{r}
#if (!require("pacman")) install.packedads("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg
               )
load(file = here::here("input/data-proc/df_study1_long_t7.RData"))

# generate analytical sample
df_study1 <- 
  df_study1_long_t7 %>%
  select(idencuesta,ola,aborto, edad, sexo, pos_id, educ, universitaria, ponderador_long_total) %>% 
  na.omit() %>% 
  mutate(ola_num=as.numeric(ola),
         ola=as.factor(ola),
         edad = case_when(edad <=23~"Between 18 and 23",
                          edad >23 & edad <=28 ~ "Between 24 and 28",
                          edad >28 & edad <=45 ~ "Between 29 and 45",
                          edad > 45 ~ "More than 45")) 

df_study1$edad <- factor(df_study1$edad, levels = c("More than 45", "Between 29 and 45", "Between 24 and 28", "Between 18 and 23"))
df_study1$sexo <- factor(df_study1$sexo, levels = c(1, 2), labels = c("Man", "Woman"))
df_study1$educ <- factor(df_study1$educ,
                         levels = c("Media o menos", "Técnica", "Universitaria"),
                         labels = c("Secondary or less", "Technical", "University or more"))
df_study1$pos_id <- factor(df_study1$pos_id,
                         levels = c("Izquierda", "Centro", "Derecha", "No se identifica"),
                         labels = c("Left", "Center", "Right", "Doesn't identify"))

marchar.null <- lmer(formula(paste0("aborto~","1 + (1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar1 <- lmer(formula(paste0("aborto~",h1,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar2 <- lmer(formula(paste0("aborto~",h2,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar3 <- lmer(formula(paste0("aborto~",h3,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar4 <- lmer(formula(paste0("aborto~",h4,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar5 <- lmer(formula(paste0("aborto~",h5,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar6 <- lmer(formula(paste0("aborto~",h6,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar7 <- lmer(formula(paste0("aborto~",h7,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar8 <- lmer(formula(paste0("aborto~",h8,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar9 <- lmer(formula(paste0("aborto~",h9,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar10 <- lmer(formula(paste0("aborto~",h10,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar11 <- lmer(formula(paste0("aborto~",h11,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar12 <- lmer(formula(paste0("aborto~",h12,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
```

## Main effects

```{r results='asis'}
ccoef <- list(
  "(Intercept)" = "Intercept",
  "ola4" = "2019",
  "ola5" = "2021",
  "ola6" = "2022",
  "ola7" = "2023",
  "edadBetween 29 and 45" = "Between 29 and 45",
  "edadBetween 24 and 28" = "Between 24 and 28",
  "edadBetween 18 and 23" = "Between 18 and 23",
  "sexoWoman" = "Woman (Ref.= Man)",
  "educTechnical" = "Technical",
  "educUniversity or more" = "University or more",
  "pos_idCenter" = "Center",
  "pos_idRight" = "Right",
  "pos_idDoesn't identify" = "Doesn't identify"
  )

texreg::knitreg(list(marchar1, marchar2, marchar3, marchar4, marchar5),
               custom.model.names = c(paste0("Model ", seq(1:5))),
               caption.above = T,
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef,
               digits = 2,
               groups = list("Wave (Ref.= 2018)" = 2:5,
                             "Age (Ref.= More than 45)" = 6:8,
                             "Education (Ref.= Secondary)" = 10:11,
                             "Political position (Ref.= Left)" = 12:14),
               custom.note = "Note: Cells contain regression coefficients with standard errors in parentheses. \n %stars.",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.80,
               include.loglik = FALSE,
               include.aic = FALSE,
               center = T,
               custom.gof.names = c("BIC", "Numb. obs.", "Num. groups: individuals", "Var: individuals (Intercept)", "Var: Residual")
               )
```

## Interaction effects 

```{r results='asis'}
ccoef2 <- list(
  "(Intercept)" = "Intercept",
  "ola4:edadBetween 29 and 45" = "2019*Age 29-45",
  "ola5:edadBetween 29 and 45" = "2021*Age 29-45",
  "ola6:edadBetween 29 and 45" = "2022*Age 29-45",
  "ola7:edadBetween 29 and 45" = "2023*Age 29-45",
  "ola4:edadBetween 24 and 28" = "2019*Age 24-28",
  "ola5:edadBetween 24 and 28" = "2021*Age 24-28",
  "ola6:edadBetween 24 and 28" = "2022*Age 24-28",
  "ola7:edadBetween 24 and 28" = "2023*Age 24-28",
  "ola4:edadBetween 18 and 23" = "2019*Age 18-23",
  "ola5:edadBetween 18 and 23" = "2021*Age 18-23",
  "ola6:edadBetween 18 and 23" = "2022*Age 18-23",
  "ola7:edadBetween 18 and 23" = "2023*Age 18-23",
  "ola4:sexoWoman" = "2019*Woman",
  "ola5:sexoWoman" = "2021*Woman",
  "ola6:sexoWoman" = "2022*Woman",
  "ola7:sexoWoman" = "2023*Woman",
  "ola4:educTechnical" = "2019*Technical",
  "ola5:educTechnical" = "2021*Technical",
  "ola6:educTechnical" = "2022*Technical",
  "ola7:educTechnical" = "2023*Technical",
  "ola4:educUniversity or more" = "2019*University",
  "ola5:educUniversity or more" = "2021*University",
  "ola6:educUniversity or more" = "2022*University",
  "ola7:educUniversity or more" = "2023*University",
  "ola4:pos_idCenter" = "2019*Center",
  "ola5:pos_idCenter" = "2021*Center",
  "ola6:pos_idCenter" = "2022*Center",
  "ola7:pos_idCenter" = "2023*Center",
  "ola4:pos_idRight" = "2019*Right",
  "ola5:pos_idRight" = "2021*Right",
  "ola6:pos_idRight" = "2022*Right",
  "ola7:pos_idRight" = "2023*Right",
  "ola4:pos_idDoesn't identify" = "2019*Doesn't identify",
  "ola5:pos_idDoesn't identify" = "2021*Doesn't identify",
  "ola6:pos_idDoesn't identify" = "2022*Doesn't identify",
  "ola7:pos_idDoesn't identify" = "2023*Doesn't identify",
  "pos_idCenter:edadBetween 29 and 45" = "Center*Age 29-45",
  "pos_idRight:edadBetween 29 and 45" = "Right*Age 29-45",
  "pos_idDoesn't identify:edadBetween 29 and 45" = "Doesn't identify * Age 29-45",
  "pos_idCenter:edadBetween 29 and 45" = "Center*Age 24-28",
  "pos_idRight:edadBetween 29 and 45" = "Right*Age 24-28",
  "pos_idDoesn't identify:edadBetween 29 and 45" = "Doesn't identify * Age 24-28",
  "pos_idCenter:edadBetween 29 and 45" = "Center*Age 18-23",
  "pos_idRight:edadBetween 29 and 45" = "Right*Age 18-23",
  "pos_idDoesn't identify:edadBetween 29 and 45" = "Doesn't identify * Age 18-23",
  "ola4:pos_idCenter:edadBetween 29 and 45" = "2019 * Center * Age 29-45",
  "ola5:pos_idCenter:edadBetween 29 and 45" = "2021 * Center * Age 29-45",
  "ola6:pos_idCenter:edadBetween 29 and 45" = "2022 * Center * Age 29-45",
  "ola7:pos_idCenter:edadBetween 29 and 45" = "2023 * Center * Age 29-45",
  "ola4:pos_idRight:edadBetween 29 and 45" = "2019 * Right * Age 29-45",
  "ola5:pos_idRight:edadBetween 29 and 45" = "2021 * Right * Age 29-45",
  "ola6:pos_idRight:edadBetween 29 and 45" = "2022 * Right * Age 29-45",
  "ola7:pos_idRight:edadBetween 29 and 45" = "2023 * Right * Age 29-45",
  "ola4:pos_idDoesn't identify:edadBetween 29 and 45" = "2019 * Doesn't identify * Age 29-45",
  "ola5:pos_idDoesn't identify:edadBetween 29 and 45" = "2021 * Doesn't identify * Age 29-45",
  "ola6:pos_idDoesn't identify:edadBetween 29 and 45" = "2022 * Doesn't identify * Age 29-45",
  "ola7:pos_idDoesn't identify:edadBetween 29 and 45" = "2023 * Doesn't identify * Age 29-45",
  "ola4:pos_idCenter:edadBetween 24 and 28" = "2019 * Center * Age 24-28",
  "ola5:pos_idCenter:edadBetween 24 and 28" = "2021 * Center * Age 24-28",
  "ola6:pos_idCenter:edadBetween 24 and 28" = "2022 * Center * Age 24-28",
  "ola7:pos_idCenter:edadBetween 24 and 28" = "2023 * Center * Age 24-28",
  "ola4:pos_idRight:edadBetween 24 and 28" = "2019 * Right * Age 24-28",
  "ola5:pos_idRight:edadBetween 24 and 28" = "2021 * Right * Age 24-28",
  "ola6:pos_idRight:edadBetween 24 and 28" = "2022 * Right * Age 24-28",
  "ola7:pos_idRight:edadBetween 24 and 28" = "2023 * Right * Age 24-28",
  "ola4:pos_idDoesn't identify:edadBetween 24 and 28" = "2019 * Doesn't identify * Age 24-28",
  "ola5:pos_idDoesn't identify:edadBetween 24 and 28" = "2021 * Doesn't identify * Age 24-28",
  "ola6:pos_idDoesn't identify:edadBetween 24 and 28" = "2022 * Doesn't identify * Age 24-28",
  "ola7:pos_idDoesn't identify:edadBetween 24 and 28" = "2023 * Doesn't identify * Age 24-28",
  "ola4:pos_idCenter:edadBetween 18 and 23" = "2019 * Center * Age 18-23",
  "ola5:pos_idCenter:edadBetween 18 and 23" = "2021 * Center * Age 18-23",
  "ola6:pos_idCenter:edadBetween 18 and 23" = "2022 * Center * Age 18-23",
  "ola7:pos_idCenter:edadBetween 18 and 23" = "2023 * Center * Age 18-23",
  "ola4:pos_idRight:edadBetween 18 and 23" = "2019 * Right * Age 18-23",
  "ola5:pos_idRight:edadBetween 18 and 23" = "2021 * Right * Age 18-23",
  "ola6:pos_idRight:edadBetween 18 and 23" = "2022 * Right * Age 18-23",
  "ola7:pos_idRight:edadBetween 18 and 23" = "2023 * Right * Age 18-23",
  "ola4:pos_idDoesn't identify:edadBetween 18 and 23" = "2019 * Doesn't identify * Age 18-23",
  "ola5:pos_idDoesn't identify:edadBetween 18 and 23" = "2021 * Doesn't identify * Age 18-23",
  "ola6:pos_idDoesn't identify:edadBetween 18 and 23" = "2022 * Doesn't identify * Age 18-23",
  "ola7:pos_idDoesn't identify:edadBetween 18 and 23" = "2023 * Doesn't identify * Age 18-23",
  "educTechnical:edadBetween 29 and 45" = "Technical * Age 29-45",
  "educUniversity or more:edadBetween 29 and 45" = "University * Age 29-45",
  "educTechnical:edadBetween 24 and 28" = "Technical * Age 24-28",
  "educUniversity or more:edadBetween 24 and 28" = "University * Age 24-28",
  "educTechnical:edadBetween 18 and 23" = "Technical * Age 18-23",
  "educUniversity or more:edadBetween 18 and 23" = "University * Age 18-23",
  "ola4:educTechnical:edadBetween 29 and 45" = "2019 * Technical * Age 29-45",
  "ola5:educTechnical:edadBetween 29 and 45" = "2021 * Technical * Age 29-45",
  "ola6:educTechnical:edadBetween 29 and 45" = "2022 * Technical * Age 29-45",
  "ola7:educTechnical:edadBetween 29 and 45" = "2023 * Technical * Age 29-45",
  "ola4:educUniversity or more:edadBetween 29 and 45" = "2019 * University * Age 29-45",
  "ola5:educUniversity or more:edadBetween 29 and 45" = "2021 * University * Age 29-45",
  "ola6:educUniversity or more:edadBetween 29 and 45" = "2022 * University * Age 29-45",
  "ola7:educUniversity or more:edadBetween 29 and 45" = "2023 * University * Age 29-45",
  "ola4:educTechnical:edadBetween 24 and 28" = "2019 * Technical * Age 24-28",
  "ola5:educTechnical:edadBetween 24 and 28" = "2021 * Technical * Age 24-28",
  "ola6:educTechnical:edadBetween 24 and 28" = "2022 * Technical * Age 24-28",
  "ola7:educTechnical:edadBetween 24 and 28" = "2023 * Technical * Age 24-28",
  "ola4:educUniversity or more:edadBetween 24 and 28" = "2019 * University * Age 24-28",
  "ola5:educUniversity or more:edadBetween 24 and 28" = "2021 * University * Age 24-28",
  "ola6:educUniversity or more:edadBetween 24 and 28" = "2022 * University * Age 24-28",
  "ola7:educUniversity or more:edadBetween 24 and 28" = "2023 * University * Age 24-28",
  "ola4:educTechnical:edadBetween 18 and 23" = "2019 * Technical * Age 18-23",
  "ola5:educTechnical:edadBetween 18 and 23" = "2021 * Technical * Age 18-23",
  "ola6:educTechnical:edadBetween 18 and 23" = "2022 * Technical * Age 18-23",
  "ola7:educTechnical:edadBetween 18 and 23" = "2023 * Technical * Age 18-23",
  "ola4:educUniversity or more:edadBetween 18 and 23" = "2019 * University * Age 18-23",
  "ola5:educUniversity or more:edadBetween 18 and 23" = "2021 * University * Age 18-23",
  "ola6:educUniversity or more:edadBetween 18 and 23" = "2022 * University * Age 18-23",
  "ola7:educUniversity or more:edadBetween 18 and 23" = "2023 * University * Age 18-23",
  "sexoWoman:edadBetween 29 and 45" = "Woman * Age 29-45",
  "sexoWoman:edadBetween 29 and 45" = "Woman * Age 24-28",
  "sexoWoman:edadBetween 29 and 45" = "Woman * Age 18-23",
  "ola4:sexoWoman:edadBetween 29 and 45" = "2019 * Woman * Age 29-45",
  "ola5:sexoWoman:edadBetween 29 and 45" = "2021 * Woman * Age 29-45",
  "ola6:sexoWoman:edadBetween 29 and 45" = "2022 * Woman * Age 29-45",
  "ola7:sexoWoman:edadBetween 29 and 45" = "2023 * Woman * Age 29-45",
  "ola4:sexoWoman:edadBetween 24 and 28" = "2019 * Woman * Age 24-28",
  "ola5:sexoWoman:edadBetween 24 and 28" = "2021 * Woman * Age 24-28",
  "ola6:sexoWoman:edadBetween 24 and 28" = "2022 * Woman * Age 24-28",
  "ola7:sexoWoman:edadBetween 24 and 28" = "2023 * Woman * Age 24-28",
  "ola4:sexoWoman:edadBetween 18 and 23" = "2019 * Woman * Age 18-23",
  "ola5:sexoWoman:edadBetween 18 and 23" = "2021 * Woman * Age 18-23",
  "ola6:sexoWoman:edadBetween 18 and 23" = "2022 * Woman * Age 18-23",
  "ola7:sexoWoman:edadBetween 18 and 23" = "2023 * Woman * Age 18-23"
  )

texreg::knitreg(list(marchar6, marchar7, marchar8, marchar9, marchar10, marchar11,marchar12),
               custom.model.names = c(paste0("Model ", seq(6:12))),
               caption.above = T,
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef2,
               digits = 2,
               custom.note = "Note: Cells contain regression coefficients with standard errors in parentheses. \n %stars.",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.80,
               include.loglik = FALSE,
               include.aic = FALSE,
               center = T,
               custom.gof.names = c("BIC", "Numb. obs.", "Num. groups: individuals", "Var: individuals (Intercept)", "Var: Residual"))
```

### Resume table

```{r}
betas <- marchar12@beta                           # Coeficientes
vcov_mat <- as.matrix(vcov(marchar12))              # Matriz de varianzas-covarianzas
ses <- sqrt(diag(vcov_mat))                         # Errores estándar
tvals <- betas / ses                              # Valores t

ses <- ses[34:45]
betas <- betas[34:45]
tvals <- tvals[34:45]

pvals <- 2 * pnorm(-abs(tvals))  # Aproximación tipo Wald (z-score)

signif_stars <- ifelse(pvals <= 0.001, "***",
                 ifelse(pvals <= 0.01, "**",
                 ifelse(pvals <= 0.05, "*", "")))

olasexoedad<-data.frame(
  Estimate = betas,
  Signif = signif_stars
)

betas <- marchar11@beta                          # Coeficientes
vcov_mat <- as.matrix(vcov(marchar11))              # Matriz de varianzas-covarianzas
ses <- sqrt(diag(vcov_mat))                         # Errores estándar
tvals <- betas / ses                              # Valores t

ses <- ses[41:64]
betas <- betas[41:64]
tvals <- tvals[41:64]

pvals <- 2 * pnorm(-abs(tvals))  # Aproximación tipo Wald (z-score)

signif_stars <- ifelse(pvals <= 0.001, "***",
                 ifelse(pvals <= 0.01, "**",
                 ifelse(pvals <= 0.05, "*", "")))

olaeducedad<-data.frame(
  Estimate = betas,
  Signif = signif_stars
)

betas <- marchar10@beta                          # Coeficientes
vcov_mat <- as.matrix(vcov(marchar10))              # Matriz de varianzas-covarianzas
ses <- sqrt(diag(vcov_mat))                         # Errores estándar
tvals <- betas / ses                              # Valores t

ses <- ses[48:83]
betas <- betas[48:83]
tvals <- tvals[48:83]

pvals <- 2 * pnorm(-abs(tvals))  # Aproximación tipo Wald (z-score)

signif_stars <- ifelse(pvals <= 0.001, "***",
                 ifelse(pvals <= 0.01, "**",
                 ifelse(pvals <= 0.05, "*", "")))

olapospoledad<-data.frame(
  Estimate = betas,
  Signif = signif_stars
)

# Woman (olasexoedad) – 12 términos
woman_idx <- c(1, 5, 9,   # 29–45
               2, 6,10,   # 24–28
               3, 7,11,   # 18–23
               4, 8,12)   # orden por ola: 2019, 2021, 2022, 2023

# Technical (olaeducedad) – 24 términos
technical_idx <- c(1, 9,17,  # 29–45
                   2,10,18,  # 24–28
                   3,11,19,  # 18–23
                   4,12,20)  # ola 2021
# university ocupa las posiciones 5:8, 13:16, 21:24
university_idx <- c(5,13,21,  # 29–45
                    6,14,22,  # 24–28
                    7,15,23,  # 18–23
                    8,16,24)

# Center (olapospoledad) – 36 términos
center_idx <- c(1,13,25,  # 29–45
                2,14,26,  # 24–28
                3,15,27,  # 18–23
                4,16,28)  # ola 2021
right_idx <-  c(5,17,29,  # 29–45
                6,18,30,
                7,19,31,
                8,20,32)
dni_idx   <-  c(9,21,33,
                10,22,34,
                11,23,35,
                12,24,36)

tabla <- cbind(
  Year = c("2019", "2019", "2019",
          "2021", "2021", "2021", 
          "2022", "2022", "2022", 
          "2023", "2023", "2023"),
  Age = rep(c("29–45", "24–28", "18–23"), times = 4),
  Woman = paste0(round(olasexoedad$Estimate[woman_idx], 2), olasexoedad$Signif[woman_idx]),
  Technical = paste0(round(olaeducedad$Estimate[technical_idx], 2), olaeducedad$Signif[technical_idx]),
  University = paste0(round(olaeducedad$Estimate[university_idx], 2), olaeducedad$Signif[university_idx]),
  Center = paste0(round(olapospoledad$Estimate[center_idx], 2), olapospoledad$Signif[center_idx]),
  Right = paste0(round(olapospoledad$Estimate[right_idx], 2), olapospoledad$Signif[right_idx]),
  `Doesnt Identify` = paste0(round(olapospoledad$Estimate[dni_idx], 2), olapospoledad$Signif[dni_idx])
)
```

```{r}
kbl(tabla, 
    align = "c") %>% 
    add_header_above(c(" " = 3,
                     "Education"=2, 
                     "Political position"=3),
                   bold = T)%>%  
  kable_paper("hover",full_width = F) %>%
     column_spec(1, bold = T) %>%
     collapse_rows(columns = 1, valign = "middle") %>% 
  footnote("***p < 0.001; **p < 0.01; *p < 0.05.")
```

## Interaction effects graphs

- Support for abortion decriminalization and age

```{r}
preds <- ggpredict(marchar6, terms = c("ola", "edad"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
 # facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Support for the legalization of abortion",
    color = "Age"
  ) +
  ylim(1, 5) +
  scale_x_discrete(labels = waves3) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Support for abortion decriminalization and sex

```{r}
preds <- ggpredict(marchar7, terms = c("ola", "sexo"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
 # facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Support for the legalization of abortion",
    color = "Sex"
  ) +
  ylim(1, 5) +
  scale_x_discrete(labels = waves3) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Support for abortion decriminalization, age and sex

```{r}
preds <- ggpredict(marchar12, terms = c("ola", "edad", "sexo"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Support for the legalization of abortion",
    color = "Age"
  ) +
  ylim(1, 5) +
  scale_x_discrete(labels = waves3) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Support for abortion decriminalization and education

```{r}
preds <- ggpredict(marchar8, terms = c("ola", "educ"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
#  facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Support for the legalization of abortion",
    color = "Education"
  ) +
  ylim(1, 5) +
  scale_x_discrete(labels = waves3) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Support for abortion decriminalization, age and education

```{r}
preds <- ggpredict(marchar11, terms = c("ola", "edad", "educ"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  facet_wrap(~ facet, ncol = 3) +
  labs(
    x = "Year",
    y = "Support for the legalization of abortion",
    color = "Age"
  ) +
  ylim(1, 5) +
  scale_x_discrete(labels = waves3) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Support for abortion decriminalization and political position

```{r}
preds <- ggpredict(marchar9, terms = c("ola", "pos_id"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
#  facet_wrap(~ facet, ncol = 3) +
  labs(
    x = "Year",
    y = "Support for the legalization of abortion",
    color = "Political position"
  ) +
  ylim(1, 5) +
  scale_x_discrete(labels = waves3) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Support for abortion decriminalization, agen and political position

```{r}
preds <- ggpredict(marchar10, terms = c("ola", "edad", "pos_id"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Support for the legalization of abortion",
    color = "edad"
  ) +
  ylim(1, 5) +
  scale_x_discrete(labels = waves3) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

# Support to student's social movement

```{r}
#if (!require("pacman")) install.packedads("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg
               )
load(file = here::here("input/data-proc/df_study1_long_t7.RData"))

# generate analytical sample
df_study1 <- 
  df_study1_long_t7 %>%
  select(idencuesta,ola,mov_estudiantil, edad, sexo, pos_id, educ, universitaria, ponderador_long_total) %>% 
  na.omit() %>% 
  mutate(ola_num=as.numeric(ola),
         ola=as.factor(ola),
         edad = case_when(edad <=23~"Between 18 and 23",
                          edad >23 & edad <=28 ~ "Between 24 and 28",
                          edad >28 & edad <=45 ~ "Between 29 and 45",
                          edad > 45 ~ "More than 45")) 

df_study1$edad <- factor(df_study1$edad, levels = c("More than 45", "Between 29 and 45", "Between 24 and 28", "Between 18 and 23"))
df_study1$sexo <- factor(df_study1$sexo, levels = c(1, 2), labels = c("Man", "Woman"))
df_study1$educ <- factor(df_study1$educ,
                         levels = c("Media o menos", "Técnica", "Universitaria"),
                         labels = c("Secondary or less", "Technical", "University or more"))
df_study1$pos_id <- factor(df_study1$pos_id,
                         levels = c("Izquierda", "Centro", "Derecha", "No se identifica"),
                         labels = c("Left", "Center", "Right", "Doesn't identify"))

marchar.null <- glmer(formula(paste0("mov_estudiantil~","1 + (1|idencuesta)")),data = df_study1, weights = ponderador_long_total, family = 'binomial')
marchar1 <- glmer(formula(paste0("mov_estudiantil~",h1,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total, family = 'binomial')
marchar2 <- glmer(formula(paste0("mov_estudiantil~",h2,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total, family = 'binomial')
marchar3 <- glmer(formula(paste0("mov_estudiantil~",h3,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total, family = 'binomial')
marchar4 <- lmer(formula(paste0("mov_estudiantil~",h4,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar5 <- lmer(formula(paste0("mov_estudiantil~",h5,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar6 <- lmer(formula(paste0("mov_estudiantil~",h6,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar7 <- lmer(formula(paste0("mov_estudiantil~",h7,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar8 <- lmer(formula(paste0("mov_estudiantil~",h8,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar9 <- lmer(formula(paste0("mov_estudiantil~",h9,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar10 <- lmer(formula(paste0("mov_estudiantil~",h10,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar11 <- lmer(formula(paste0("mov_estudiantil~",h11,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
marchar12 <- lmer(formula(paste0("mov_estudiantil~",h12,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
```

## Main effects

```{r results='asis'}
ccoef <- list(
  "(Intercept)" = "Intercept",
  "ola2" = "2017",
  "ola3" = "2018",
  "ola4" = "2019",
  "ola5" = "2021",
  "ola6" = "2022",
  "ola7" = "2023",
  "edadBetween 29 and 45" = "Between 29 and 45",
  "edadBetween 24 and 28" = "Between 24 and 28",
  "edadBetween 18 and 23" = "Between 18 and 23",
  "sexoWoman" = "Woman (Ref.= Man)",
  "educTechnical" = "Technical",
  "educUniversity or more" = "University or more",
  "pos_idCenter" = "Center",
  "pos_idRight" = "Right",
  "pos_idDoesn't identify" = "Doesn't identify"
  )

texreg::knitreg(list(marchar1, marchar2, marchar3, marchar4, marchar5),
               custom.model.names = c(paste0("Model ", seq(1:5))),
               caption.above = T,
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef,
               digits = 2,
               groups = list("Wave (Ref.= 2016)" = 2:7,
                             "Age (Ref.= More than 45)" = 8:10,
                             "Education (Ref.= Secondary)" = 12:13,
                             "Political position (Ref.= Left)" = 14:16),
               custom.note = "Note: Cells contain regression coefficients with standard errors in parentheses. \n %stars.",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.80,
               include.loglik = FALSE,
               include.aic = FALSE,
               center = T,
               custom.gof.names = c("BIC", "Numb. obs.", "Num. groups: individuals", "Var: individuals (Intercept)", "Var: Residual")
               )
```

## Interaction effects

```{r results='asis'}
ccoef2 <- list(
  "(Intercept)" = "Intercept",
  "ola2:edadBetween 29 and 45" = "2017*Age 29-45",
  "ola3:edadBetween 29 and 45" = "2018*Age 29-45",
  "ola4:edadBetween 29 and 45" = "2019*Age 29-45",
  "ola5:edadBetween 29 and 45" = "2021*Age 29-45",
  "ola6:edadBetween 29 and 45" = "2022*Age 29-45",
  "ola7:edadBetween 29 and 45" = "2023*Age 29-45",
  "ola2:edadBetween 24 and 28" = "2017*Age 24-28",
  "ola3:edadBetween 24 and 28" = "2018*Age 24-28",
  "ola4:edadBetween 24 and 28" = "2019*Age 24-28",
  "ola5:edadBetween 24 and 28" = "2021*Age 24-28",
  "ola6:edadBetween 24 and 28" = "2022*Age 24-28",
  "ola7:edadBetween 24 and 28" = "2023*Age 24-28",
  "ola2:edadBetween 18 and 23" = "2017*Age 18-23",
  "ola3:edadBetween 18 and 23" = "2018*Age 18-23",
  "ola4:edadBetween 18 and 23" = "2019*Age 18-23",
  "ola5:edadBetween 18 and 23" = "2021*Age 18-23",
  "ola6:edadBetween 18 and 23" = "2022*Age 18-23",
  "ola7:edadBetween 18 and 23" = "2023*Age 18-23",
  "ola2:sexoWoman" = "2017*Woman",
  "ola3:sexoWoman" = "2018*Woman",
  "ola4:sexoWoman" = "2019*Woman",
  "ola5:sexoWoman" = "2021*Woman",
  "ola6:sexoWoman" = "2022*Woman",
  "ola7:sexoWoman" = "2023*Woman",
  "ola2:educTechnical" = "2017*Technical",
  "ola3:educTechnical" = "2018*Technical",
  "ola4:educTechnical" = "2019*Technical",
  "ola5:educTechnical" = "2021*Technical",
  "ola6:educTechnical" = "2022*Technical",
  "ola7:educTechnical" = "2023*Technical",
  "ola2:educUniversity or more" = "2017*University",
  "ola3:educUniversity or more" = "2018*University",
  "ola4:educUniversity or more" = "2019*University",
  "ola5:educUniversity or more" = "2021*University",
  "ola6:educUniversity or more" = "2022*University",
  "ola7:educUniversity or more" = "2023*University",
  "ola2:pos_idCenter" = "2017*Center",
  "ola3:pos_idCenter" = "2018*Center",
  "ola4:pos_idCenter" = "2019*Center",
  "ola5:pos_idCenter" = "2021*Center",
  "ola6:pos_idCenter" = "2022*Center",
  "ola7:pos_idCenter" = "2023*Center",
  "ola2:pos_idRight" = "2017*Right",
  "ola3:pos_idRight" = "2018*Right",
  "ola4:pos_idRight" = "2019*Right",
  "ola5:pos_idRight" = "2021*Right",
  "ola6:pos_idRight" = "2022*Right",
  "ola7:pos_idRight" = "2023*Right",
  "ola2:pos_idDoesn't identify" = "2017*Doesn't identify",
  "ola3:pos_idDoesn't identify" = "2018*Doesn't identify",
  "ola4:pos_idDoesn't identify" = "2019*Doesn't identify",
  "ola5:pos_idDoesn't identify" = "2021*Doesn't identify",
  "ola6:pos_idDoesn't identify" = "2022*Doesn't identify",
  "ola7:pos_idDoesn't identify" = "2023*Doesn't identify",
  "pos_idCenter:edadBetween 29 and 45" = "Center*Age 29-45",
  "pos_idRight:edadBetween 29 and 45" = "Right*Age 29-45",
  "pos_idDoesn't identify:edadBetween 29 and 45" = "Doesn't identify * Age 29-45",
  "pos_idCenter:edadBetween 29 and 45" = "Center*Age 24-28",
  "pos_idRight:edadBetween 29 and 45" = "Right*Age 24-28",
  "pos_idDoesn't identify:edadBetween 29 and 45" = "Doesn't identify * Age 24-28",
  "pos_idCenter:edadBetween 29 and 45" = "Center*Age 18-23",
  "pos_idRight:edadBetween 29 and 45" = "Right*Age 18-23",
  "pos_idDoesn't identify:edadBetween 29 and 45" = "Doesn't identify * Age 18-23",
  "ola2:pos_idCenter:edadBetween 29 and 45" = "2017 * Center * Age 29-45",
  "ola3:pos_idCenter:edadBetween 29 and 45" = "2018 * Center * Age 29-45",
  "ola4:pos_idCenter:edadBetween 29 and 45" = "2019 * Center * Age 29-45",
  "ola5:pos_idCenter:edadBetween 29 and 45" = "2021 * Center * Age 29-45",
  "ola6:pos_idCenter:edadBetween 29 and 45" = "2022 * Center * Age 29-45",
  "ola7:pos_idCenter:edadBetween 29 and 45" = "2023 * Center * Age 29-45",
  "ola2:pos_idRight:edadBetween 29 and 45" = "2017 * Right * Age 29-45",
  "ola3:pos_idRight:edadBetween 29 and 45" = "2018 * Right * Age 29-45",
  "ola4:pos_idRight:edadBetween 29 and 45" = "2019 * Right * Age 29-45",
  "ola5:pos_idRight:edadBetween 29 and 45" = "2021 * Right * Age 29-45",
  "ola6:pos_idRight:edadBetween 29 and 45" = "2022 * Right * Age 29-45",
  "ola7:pos_idRight:edadBetween 29 and 45" = "2023 * Right * Age 29-45",
  "ola2:pos_idDoesn't identify:edadBetween 29 and 45" = "2017 * Doesn't identify * Age 29-45",
  "ola3:pos_idDoesn't identify:edadBetween 29 and 45" = "2018 * Doesn't identify * Age 29-45",
  "ola4:pos_idDoesn't identify:edadBetween 29 and 45" = "2019 * Doesn't identify * Age 29-45",
  "ola5:pos_idDoesn't identify:edadBetween 29 and 45" = "2021 * Doesn't identify * Age 29-45",
  "ola6:pos_idDoesn't identify:edadBetween 29 and 45" = "2022 * Doesn't identify * Age 29-45",
  "ola7:pos_idDoesn't identify:edadBetween 29 and 45" = "2023 * Doesn't identify * Age 29-45",
  "ola2:pos_idCenter:edadBetween 24 and 28" = "2017 * Center * Age 24-28",
  "ola3:pos_idCenter:edadBetween 24 and 28" = "2018 * Center * Age 24-28",
  "ola4:pos_idCenter:edadBetween 24 and 28" = "2019 * Center * Age 24-28",
  "ola5:pos_idCenter:edadBetween 24 and 28" = "2021 * Center * Age 24-28",
  "ola6:pos_idCenter:edadBetween 24 and 28" = "2022 * Center * Age 24-28",
  "ola7:pos_idCenter:edadBetween 24 and 28" = "2023 * Center * Age 24-28",
  "ola2:pos_idRight:edadBetween 24 and 28" = "2017 * Right * Age 24-28",
  "ola3:pos_idRight:edadBetween 24 and 28" = "2018 * Right * Age 24-28",
  "ola4:pos_idRight:edadBetween 24 and 28" = "2019 * Right * Age 24-28",
  "ola5:pos_idRight:edadBetween 24 and 28" = "2021 * Right * Age 24-28",
  "ola6:pos_idRight:edadBetween 24 and 28" = "2022 * Right * Age 24-28",
  "ola7:pos_idRight:edadBetween 24 and 28" = "2023 * Right * Age 24-28",
  "ola2:pos_idDoesn't identify:edadBetween 24 and 28" = "2017 * Doesn't identify * Age 24-28",
  "ola3:pos_idDoesn't identify:edadBetween 24 and 28" = "2018 * Doesn't identify * Age 24-28",
  "ola4:pos_idDoesn't identify:edadBetween 24 and 28" = "2019 * Doesn't identify * Age 24-28",
  "ola5:pos_idDoesn't identify:edadBetween 24 and 28" = "2021 * Doesn't identify * Age 24-28",
  "ola6:pos_idDoesn't identify:edadBetween 24 and 28" = "2022 * Doesn't identify * Age 24-28",
  "ola7:pos_idDoesn't identify:edadBetween 24 and 28" = "2023 * Doesn't identify * Age 24-28",
  "ola2:pos_idCenter:edadBetween 18 and 23" = "2017 * Center * Age 18-23",
  "ola3:pos_idCenter:edadBetween 18 and 23" = "2018 * Center * Age 18-23",
  "ola4:pos_idCenter:edadBetween 18 and 23" = "2019 * Center * Age 18-23",
  "ola5:pos_idCenter:edadBetween 18 and 23" = "2021 * Center * Age 18-23",
  "ola6:pos_idCenter:edadBetween 18 and 23" = "2022 * Center * Age 18-23",
  "ola7:pos_idCenter:edadBetween 18 and 23" = "2023 * Center * Age 18-23",
  "ola2:pos_idRight:edadBetween 18 and 23" = "2017 * Right * Age 18-23",
  "ola3:pos_idRight:edadBetween 18 and 23" = "2018 * Right * Age 18-23",
  "ola4:pos_idRight:edadBetween 18 and 23" = "2019 * Right * Age 18-23",
  "ola5:pos_idRight:edadBetween 18 and 23" = "2021 * Right * Age 18-23",
  "ola6:pos_idRight:edadBetween 18 and 23" = "2022 * Right * Age 18-23",
  "ola7:pos_idRight:edadBetween 18 and 23" = "2023 * Right * Age 18-23",
  "ola2:pos_idDoesn't identify:edadBetween 18 and 23" = "2017 * Doesn't identify * Age 18-23",
  "ola3:pos_idDoesn't identify:edadBetween 18 and 23" = "2018 * Doesn't identify * Age 18-23",
  "ola4:pos_idDoesn't identify:edadBetween 18 and 23" = "2019 * Doesn't identify * Age 18-23",
  "ola5:pos_idDoesn't identify:edadBetween 18 and 23" = "2021 * Doesn't identify * Age 18-23",
  "ola6:pos_idDoesn't identify:edadBetween 18 and 23" = "2022 * Doesn't identify * Age 18-23",
  "ola7:pos_idDoesn't identify:edadBetween 18 and 23" = "2023 * Doesn't identify * Age 18-23",
  "educTechnical:edadBetween 29 and 45" = "Technical * Age 29-45",
  "educUniversity or more:edadBetween 29 and 45" = "University * Age 29-45",
  "educTechnical:edadBetween 24 and 28" = "Technical * Age 24-28",
  "educUniversity or more:edadBetween 24 and 28" = "University * Age 24-28",
  "educTechnical:edadBetween 18 and 23" = "Technical * Age 18-23",
  "educUniversity or more:edadBetween 18 and 23" = "University * Age 18-23",
  "ola2:educTechnical:edadBetween 29 and 45" = "2017 * Technical * Age 29-45",
  "ola3:educTechnical:edadBetween 29 and 45" = "2018 * Technical * Age 29-45",
  "ola4:educTechnical:edadBetween 29 and 45" = "2019 * Technical * Age 29-45",
  "ola5:educTechnical:edadBetween 29 and 45" = "2021 * Technical * Age 29-45",
  "ola6:educTechnical:edadBetween 29 and 45" = "2022 * Technical * Age 29-45",
  "ola7:educTechnical:edadBetween 29 and 45" = "2023 * Technical * Age 29-45",
  "ola2:educUniversity or more:edadBetween 29 and 45" = "2017 * University * Age 29-45",
  "ola3:educUniversity or more:edadBetween 29 and 45" = "2018 * University * Age 29-45",
  "ola4:educUniversity or more:edadBetween 29 and 45" = "2019 * University * Age 29-45",
  "ola5:educUniversity or more:edadBetween 29 and 45" = "2021 * University * Age 29-45",
  "ola6:educUniversity or more:edadBetween 29 and 45" = "2022 * University * Age 29-45",
  "ola7:educUniversity or more:edadBetween 29 and 45" = "2023 * University * Age 29-45",
  "ola2:educTechnical:edadBetween 24 and 28" = "2017 * Technical * Age 24-28",
  "ola3:educTechnical:edadBetween 24 and 28" = "2018 * Technical * Age 24-28",
  "ola4:educTechnical:edadBetween 24 and 28" = "2019 * Technical * Age 24-28",
  "ola5:educTechnical:edadBetween 24 and 28" = "2021 * Technical * Age 24-28",
  "ola6:educTechnical:edadBetween 24 and 28" = "2022 * Technical * Age 24-28",
  "ola7:educTechnical:edadBetween 24 and 28" = "2023 * Technical * Age 24-28",
  "ola2:educUniversity or more:edadBetween 24 and 28" = "2017 * University * Age 24-28",
  "ola3:educUniversity or more:edadBetween 24 and 28" = "2018 * University * Age 24-28",
  "ola4:educUniversity or more:edadBetween 24 and 28" = "2019 * University * Age 24-28",
  "ola5:educUniversity or more:edadBetween 24 and 28" = "2021 * University * Age 24-28",
  "ola6:educUniversity or more:edadBetween 24 and 28" = "2022 * University * Age 24-28",
  "ola7:educUniversity or more:edadBetween 24 and 28" = "2023 * University * Age 24-28",
  "ola2:educTechnical:edadBetween 18 and 23" = "2017 * Technical * Age 18-23",
  "ola3:educTechnical:edadBetween 18 and 23" = "2018 * Technical * Age 18-23",
  "ola4:educTechnical:edadBetween 18 and 23" = "2019 * Technical * Age 18-23",
  "ola5:educTechnical:edadBetween 18 and 23" = "2021 * Technical * Age 18-23",
  "ola6:educTechnical:edadBetween 18 and 23" = "2022 * Technical * Age 18-23",
  "ola7:educTechnical:edadBetween 18 and 23" = "2023 * Technical * Age 18-23",
  "ola2:educUniversity or more:edadBetween 18 and 23" = "2017 * University * Age 18-23",
  "ola3:educUniversity or more:edadBetween 18 and 23" = "2018 * University * Age 18-23",
  "ola4:educUniversity or more:edadBetween 18 and 23" = "2019 * University * Age 18-23",
  "ola5:educUniversity or more:edadBetween 18 and 23" = "2021 * University * Age 18-23",
  "ola6:educUniversity or more:edadBetween 18 and 23" = "2022 * University * Age 18-23",
  "ola7:educUniversity or more:edadBetween 18 and 23" = "2023 * University * Age 18-23",
  "sexoWoman:edadBetween 29 and 45" = "Woman * Age 29-45",
  "sexoWoman:edadBetween 29 and 45" = "Woman * Age 24-28",
  "sexoWoman:edadBetween 29 and 45" = "Woman * Age 18-23",
  "ola2:sexoWoman:edadBetween 29 and 45" = "2017 * Woman * Age 29-45",
  "ola3:sexoWoman:edadBetween 29 and 45" = "2018 * Woman * Age 29-45",
  "ola4:sexoWoman:edadBetween 29 and 45" = "2019 * Woman * Age 29-45",
  "ola5:sexoWoman:edadBetween 29 and 45" = "2021 * Woman * Age 29-45",
  "ola6:sexoWoman:edadBetween 29 and 45" = "2022 * Woman * Age 29-45",
  "ola7:sexoWoman:edadBetween 29 and 45" = "2023 * Woman * Age 29-45",
  "ola2:sexoWoman:edadBetween 24 and 28" = "2017 * Woman * Age 24-28",
  "ola3:sexoWoman:edadBetween 24 and 28" = "2018 * Woman * Age 24-28",
  "ola4:sexoWoman:edadBetween 24 and 28" = "2019 * Woman * Age 24-28",
  "ola5:sexoWoman:edadBetween 24 and 28" = "2021 * Woman * Age 24-28",
  "ola6:sexoWoman:edadBetween 24 and 28" = "2022 * Woman * Age 24-28",
  "ola7:sexoWoman:edadBetween 24 and 28" = "2023 * Woman * Age 24-28",
  "ola2:sexoWoman:edadBetween 18 and 23" = "2017 * Woman * Age 18-23",
  "ola3:sexoWoman:edadBetween 18 and 23" = "2018 * Woman * Age 18-23",
  "ola4:sexoWoman:edadBetween 18 and 23" = "2019 * Woman * Age 18-23",
  "ola5:sexoWoman:edadBetween 18 and 23" = "2021 * Woman * Age 18-23",
  "ola6:sexoWoman:edadBetween 18 and 23" = "2022 * Woman * Age 18-23",
  "ola7:sexoWoman:edadBetween 18 and 23" = "2023 * Woman * Age 18-23"
  )

texreg::knitreg(list(marchar6, marchar7, marchar8, marchar9, marchar10, marchar11,marchar12),
               custom.model.names = c(paste0("Model ", seq(6:12))),
               caption.above = T,
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef2,
               digits = 2,
               custom.note = "Note: Cells contain regression coefficients with standard errors in parentheses. \n %stars.",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.80,
               include.loglik = FALSE,
               include.aic = FALSE,
               center = T,
               custom.gof.names = c("BIC", "Numb. obs.", "Num. groups: individuals", "Var: individuals (Intercept)", "Var: Residual"))
```

### Resume table

```{r}
betas <- marchar12@beta                           # Coeficientes
vcov_mat <- as.matrix(vcov(marchar12))              # Matriz de varianzas-covarianzas
ses <- sqrt(diag(vcov_mat))                         # Errores estándar
tvals <- betas / ses                              # Valores t

ses <- ses[44:61]
betas <- betas[44:61]
tvals <- tvals[44:61]

pvals <- 2 * pnorm(-abs(tvals))  # Aproximación tipo Wald (z-score)

signif_stars <- ifelse(pvals <= 0.001, "***",
                 ifelse(pvals <= 0.01, "**",
                 ifelse(pvals <= 0.05, "*", "")))

olasexoedad<-data.frame(
  Estimate = betas,
  Signif = signif_stars
)

betas <- marchar11@beta                          # Coeficientes
vcov_mat <- as.matrix(vcov(marchar11))              # Matriz de varianzas-covarianzas
ses <- sqrt(diag(vcov_mat))                         # Errores estándar
tvals <- betas / ses                              # Valores t

ses <- ses[53:88]
betas <- betas[53:88]
tvals <- tvals[53:88]

pvals <- 2 * pnorm(-abs(tvals))  # Aproximación tipo Wald (z-score)

signif_stars <- ifelse(pvals <= 0.001, "***",
                 ifelse(pvals <= 0.01, "**",
                 ifelse(pvals <= 0.05, "*", "")))

olaeducedad<-data.frame(
  Estimate = betas,
  Signif = signif_stars
)

betas <- marchar10@beta                          # Coeficientes
vcov_mat <- as.matrix(vcov(marchar10))              # Matriz de varianzas-covarianzas
ses <- sqrt(diag(vcov_mat))                         # Errores estándar
tvals <- betas / ses                              # Valores t

ses <- ses[62:115]
betas <- betas[62:115]
tvals <- tvals[62:115]

pvals <- 2 * pnorm(-abs(tvals))  # Aproximación tipo Wald (z-score)

signif_stars <- ifelse(pvals <= 0.001, "***",
                 ifelse(pvals <= 0.01, "**",
                 ifelse(pvals <= 0.05, "*", "")))

olapospoledad<-data.frame(
  Estimate = betas,
  Signif = signif_stars
)

# Woman (olasexoedad)
woman_idx <- c(1, 7, 13, 2, 8, 14, 3, 9, 15, 4, 10, 16, 5, 11, 17, 6, 12, 18)

# Technical (olaeducedad)
technical_idx <- c(1, 13, 25, 2, 14, 26, 3, 15, 27, 4, 16, 28, 5, 17, 29, 6, 18, 30)

# University (olaeducedad)
university_idx <- c(7, 19, 31, 8, 20, 32, 9, 21, 33, 10, 22, 34, 11, 23, 35, 12, 24, 36)

# Edad 29–45 → posiciones: 1, 19, 37, 2, 20, 38, 3, 21, 39, ...
center_idx <- c(1, 19, 37, 2, 20, 38, 3, 21, 39, 4, 22, 40, 5, 23, 41, 6, 24, 42)
right_idx  <- c(7, 25, 43, 8, 26, 44, 9, 27, 45,10, 28, 46,11, 29, 47,12, 30, 48)
dni_idx    <- c(13, 31, 49,14, 32, 50,15, 33, 51,16, 34, 52,17, 35, 53,18, 36, 54)




tabla <- cbind(
  Year = c("2017", "2017", "2017", 
          "2018", "2018", "2018",
          "2019", "2019", "2019",
          "2021", "2021", "2021", 
          "2022", "2022", "2022", 
          "2023", "2023", "2023"),
  Age = rep(c("29–45", "24–28", "18–23"), times = 6),
  Woman = paste0(round(olasexoedad$Estimate[woman_idx], 2), olasexoedad$Signif[woman_idx]),
  Technical = paste0(round(olaeducedad$Estimate[technical_idx], 2), olaeducedad$Signif[technical_idx]),
  University = paste0(round(olaeducedad$Estimate[university_idx], 2), olaeducedad$Signif[university_idx]),
  Center = paste0(round(olapospoledad$Estimate[center_idx], 2), olapospoledad$Signif[center_idx]),
  Right = paste0(round(olapospoledad$Estimate[right_idx], 2), olapospoledad$Signif[right_idx]),
  `Doesnt Identify` = paste0(round(olapospoledad$Estimate[dni_idx], 2), olapospoledad$Signif[dni_idx])
)
```

```{r}
kbl(tabla, 
    align = "c") %>% 
    add_header_above(c(" " = 3,
                     "Education"=2, 
                     "Political position"=3),
                   bold = T)%>%  
  kable_paper("hover",full_width = F) %>%
     column_spec(1, bold = T) %>%
     collapse_rows(columns = 1, valign = "middle") %>% 
  footnote("***p < 0.001; **p < 0.01; *p < 0.05.")
```

## Interaction effects graphs

- Support to student’s social movement and age

```{r}
preds <- ggpredict(marchar6, terms = c("ola", "edad"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
 # facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Support for the student movement",
    color = "Age"
  ) +
  ylim(0, 1) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Support to student’s social movement and sex

```{r}
preds <- ggpredict(marchar7, terms = c("ola", "sexo"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
 # facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Support for the student movement",
    color = "Sex"
  ) +
  ylim(0, 1) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Support to student’s social movement, age and sex

```{r}
preds <- ggpredict(marchar12, terms = c("ola", "edad", "sexo"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Support for the student movement",
    color = "Age"
  ) +
  ylim(0, 1) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Support to student’s social movement and education

```{r}
preds <- ggpredict(marchar8, terms = c("ola", "educ"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
#  facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Support for the student movement",
    color = "Education"
  ) +
  ylim(0, 1) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Support to student’s social movement, age and education

```{r}
preds <- ggpredict(marchar11, terms = c("ola", "edad", "educ"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  facet_wrap(~ facet, ncol = 3) +
  labs(
    x = "Year",
    y = "Support for the student movement",
    color = "Age"
  ) +
  ylim(0, 1) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Support to student’s social movement and political position

```{r}
preds <- ggpredict(marchar9, terms = c("ola", "pos_id"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
#  facet_wrap(~ facet, ncol = 3) +
  labs(
    x = "Year",
    y = "Support for the student movement",
    color = "Political position"
  ) +
  ylim(0, 1) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

- Support to student’s social movement, age and political position

```{r}
preds <- ggpredict(marchar10, terms = c("ola", "edad", "pos_id"))

ggplot(preds, aes(x = x, y = predicted, color = group, group = group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  facet_wrap(~ facet, ncol = 2) +
  labs(
    x = "Year",
    y = "Support for the student movement",
    color = "edad"
  ) +
  ylim(-0.3, 1) +
  scale_x_discrete(labels = waves) + 
  theme_minimal() +
  theme(legend.position = "bottom")
```

